\begin{footnotesize}
\begin{description}[%
			%	style=multiline,
				style=nextline,
				leftmargin=3cm,
				font=\normalfont]
\item[AA-long] Archäologischer Anzeiger 
\item[AAA-long] Αρχαιολογικά Ανάλεκτα εξ Αθηνών 
\item[AAcque-long] Archeologia delle acque. Rivista semestrale di antropologia, archeologia, etnografia, storia dell'acqua 
\item[AAdv-long] The Archaeological Advertiser 
\item[AAJ-long] Annual of the Department of Antiquities of Jordan 
\item[AAlpi-long] Archeologia delle Alpi 
\item[AarbKob-long] Aarbøger for nordisk oldkyndighed og historie %*Abweichung!
\item[AArchit-long] Archeologia dell'architettura 
\item[AAS-long] Les annales archéologiques arabes syriennes 
\item[AASOR-long] The Annual of the American Schools of Oriental Research 
\item[AAusgrBadWuert-long] Archäologische Ausgrabungen in Baden-Württemberg %*Abweichung!
\item[AAustr-long] Archaeologia Austriaca 
\item[ABADY-long] Archäologische Berichte aus dem Yemen 
\item[AbhBerlin-long] Abhandlungen der Deutschen Akademie der Wissenschaften zu Berlin 
\item[AbhDuesseldorf-long] Abhandlungen der Rheinisch-Westfälischen Akademie der Wissenschaften %*Abweichung!
\item[AbhGoettingen-long] Abhandlungen der Akademie der Wissenschaften zu Göttingen. Philologisch-Historische Klasse %*Abweichung!
\item[AbhLeipzig-long] Abhandlungen der Sächsischen Akademie der Wissenschaften zu Leipzig. Philologisch-Historische Klasse 
\item[AbhMainz-long] Akademie der Wissenschaften und der Literatur in Mainz. Abhandlungen der Geistes- und Sozialwissenschaftlichen Klasse 
\item[AbhMuenchen-long] Bayerische Akademie der Wissenschaften. Philosophisch-Historische Klasse. Abhandlungen %*Abweichung!
\item[ABret-long] Archéologie en Bretagne. Bulletin d'information 
\item[Abr-Nahrain-long] Abr-Nahrain. An Annual Published by the Department of Middle Eastern Studies, University of Melbourne 
\item[ABulg-long] Archaeologia Bulgarica 
\item[ABV-long] J. D. Beazley, Attic Black-figure Vase-painters (Oxford 1956) 
\item[ACalc-long] Archeologia e calcolatori 
\item[ACamp-long] Archeologia in Campania. Bolletino di informazioni a cura della Soprintendenza archeologica delle province di Napoli e Caserta 
\item[ACant-long] Archaeologia Cantiana 
\item[AcBibl-long] Accademie e biblioteche d'Italia 
\item[Achse-long] Achse, Rad und Wagen. Beiträge zur Geschichte der Landfahrzeuge 
\item[Acme-long] Acme. Annali della Facoltà di lettere e filosofia dell'Università degli studi di Milano 
\item[Acontia-long] Acontia. Revista de arqueología 
\item[ACors-long] Archeologia corsa 
\item[ActaAArtHist-long] Acta ad archaeologiam et artium historiam pertinentia 
\item[ActaAArtHist-sa-long] Acta ad archaeologiam et artium historiam pertinentia. Series altera in 8 %*Abweichung!
\item[ActaAcAbo-long] Acta Academiae Aboensis 
\item[ActaACarp-long] Acta archaeologica Carpathica 
\item[ActaALov-long] Acta archaeologica Lovaniensia 
\item[ActaALovMono-long] Acta archaeologica Lovaniensia. Monographiae 
\item[ActaAntHung-long] Acta antiqua Academiae scientiarum Hungaricae 
\item[ActaArch-long] Acta archaeologica. København 
\item[ActaArchHung-long] Acta archaeologica Academiae scientiarum Hungaricae 
\item[ActaAth-long] Acta Instituti Atheniensis regni Sueciae 
\item[ActaCl-long] Acta classica. Proceedings of the Classical Association of South Africa 
\item[ActaClDebrec-long] Acta classica Universitatis scientiarum Debreceniensis 
\item[ActaHistDac-long] Acta historica. Societas academica Dacoromana 
\item[ActaHyp-long] Acta hyperborea. Danish Studies in Classical Archaeology 
\item[ActaInstRomFin-long] Acta Instituti Romani Finlandiae 
\item[ActaMusNapoca-long] Acta Musei Napocensis 
\item[ActaMusPorol-long] Acta Musei Porolissensis 
\item[ActaNum-long] Acta numismática (Barcelona) 
\item[ActaOr-long] Acta orientalia (Kopenhagen) 
\item[ActaOrHung-long] Acta orientalia Academiae scientiarum Hungaricae 
\item[ActaPhilSocDac-long] Acta philologica. Societas academica Dacoromana 
\item[ActaPraehistA-long] Acta praehistorica et archaeologica 
\item[ActaTorunA-long] Acta Universitatis Nicolai Copernici. Archaeologia 
\item[ActaTorunHist-long] Acta Universitatis Nicolai Copernici. Historia 
\item[AD-long] Antike Denkmäler 
\item[ADAIK-long] Abhandlungen des Deutschen Archäologischen Instituts, Abteilung Kairo 
\item[Adalya-long] Adalya. Annual of the Suna \& Inan Kiraç-Research Institute on Mediterranean Civilizations 
\item[ADelt-A-long] Αρχαιολογικόν Δελτίον (Μελέτες) %*Abweichung!
\item[ADelt-B-long] Αρχαιολογικόν Δελτίον (Χρονικά) %*Abweichung!
\item[ADerg-long] Arkeoloji dergisi. Ege Üniversitesi Edebiyat Fakültesi 
\item[ADFU-long] Ausgrabungen der Deutschen Forschungsgemeinschaft in Uruk-Warka 
\item[AdI-long] Annali dell'Instituto di corrispondenza archeologica 
\item[ADOG-long] Abhandlungen der Deutschen Orient-Gesellschaft 
\item[Adumatu-long] Adumatu. A Semi-Annual Archeological Refereed Journal on the Arab World 
\item[AE-long] L'année épigraphique 
\item[AeA-long] Aegean Archaeology 
\item[Aegaeum-long] Aegaeum. Annales d'archéologie égéenne de l'Université de Liège 
\item[AegLev-long] Ägypten und Levante. Egypt and the Levant. Internationale Zeitschrift für ägyptische Archäologie und deren Nachbargebiete %*Abweichung!
\item[AEmil-long] Archeologia dell'Emilia-Romagna 
\item[AEphem-long] Αρχαιολογική Eφημερίς 
\item[AeR-long] Atene e Roma 
\item[AErgoMak-long] Το Αρχαιολογικό Έργο στη Μακεδονία και Θράκη 
\item[AErt-long] Archaeologiai értesitő
\item[AEspA-long] Archivo español de arqueología 
\item[Aevum-long] Aevum. Rassegna di scienze storiche linguistiche e filologiche 
\item[AevumAnt-long] Aevum antiquum 
\item[AF-long] Archäologische Forschungen 
\item[AfO-long] Archiv für Orientforschung 
\item[Africa-long] Africa. Institut national d'archéologie et d'art, Tunis 
\item[AGD-long] Antike Gemmen in deutschen Sammlungen 
\item[AGeo-long] Archaeologia geographica 
\item[Agora-long] The Athenian Agora 
\item[AgoraPB-long] Excavations of the Athenian Agora. Picture Book 
\item[AHist-long] Arqueologia e história 
\item[AHistStAlex-long] Archaeological and Historical Studies. The Archaeological Society of Alexandria 
\item[AHw-long] W. von Soden, Akkadisches Handwörterbuch (Wiesbaden 1965--1981) 
\item[AiD-long] Archäologie in Deutschland 
\item[AInf-long] Archäologische Informationen. Mitteilungen zur Ur- und Frühgeschichte 
\item[AIONArch-long] Annali dell'Istituto universitario orientale di Napoli. Dipartimento di studi del mondo classico e del Mediterraneo antico. Sezione di archeologia e storia antica 
\item[AIONFil-long] Annali dell'Istituto universitario orientale di Napoli. Dipartimento di studi del mondo classico e del Mediterraneo antico. Sezione filologicoletteraria 
\item[AIONLing-long] Annali dell'Istituto universitario orientale di Napoli. Dipartimento di studi del mondo classico e del Mediterraneo antico. Sezione linguistica 
\item[AIPhOr-long] Annuaire de l'Institut de philologie et d'histoire orientales et slaves (Université Libre de Bruxelles) 
\item[Aitna-long] Aitna. Quaderni di topografia antica 
\item[AJA-long] American Journal of Archaeology 
\item[AJahrBay-long] Das archäologische Jahr in Bayern 
\item[AJPh-long] American Journal of Philology 
\item[AJug-long] Archaeologia Jugoslavica 
\item[AKorrBl-long] Archäologisches Korrespondenzblatt 
\item[AlbaRegia-long] Alba Regia. Annales Musei Stephani regis 
\item[AlmaMaterSt-long] Alma mater studiorum Almanacco calabrese Almoraima 
\item[AlmanachWien-long] Österreichische Akademie der Wissenschaften. Almanach 
\item[AlonJisrael-long] Alon mahleqat ha-'atiqot šel medinat Jisra'el 
\item[Al-Qannis-long] Al-Qanniš. Boletín del Taller de arqueología de Alcañiz
\item[Altamura-long] Altamura. Bollettino dell'Archivio-biblioteca-museo civico 
\item[AltoMed-long] Alto medioevo 
\item[Alt-Paphos-long] Ausgrabungen in Alt-Paphos auf Cypern 
\item[AltThuer-long] Alt-Thüringen %*Abweichung!
\item[AM-long] Mitteilungen des Deutschen Archäologischen Instituts, Athenische Abteilung 
\item[AMediev-long] Archaeologia medievale. Cultura materiale, insediamenti, territorio 
\item[AMethTh-long] Advances in Archaeological Method and Theory 
\item[AMI-long] Archäologische Mitteilungen aus Iran 
\item[AMIT-long] Archäologische Mitteilungen aus Iran und Turan 
\item[AmJAncHist-long] American Journal of Ancient History 
\item[AmJNum-long] American Journal of Numismatics 
\item[AMold-long] Arheologia Moldovei 
\item[AMosel-long] Archaeologia Mosellana 
\item[AMS-long] Asia Minor Studien 
\item[AmStP-long] American Studies in Papyrology 
\item[AMuGS-long] Antike Münzen und geschnittene Steine 
\item[ANachr-long] Archäologisches Nachrichtenblatt 
\item[ANachrBad-long] Archäologische Nachrichten aus Baden 
\item[AnadoluAra-long] Anadolu araştırmaları. Jahrbuch für kleinasiatische Forschung 
\item[AnadoluKonf-long] Anadolu Medeniyetleri Müzesi konferansları 
\item[AnadoluYil-long] Anadolu Medeniyetleri Müzesi yıllığı 
\item[AnAe-long] Analecta Aegyptiaca 
\item[Anagennesis-long] Anagennesis. A Papyrological Journal 
\item[AnalBolland-long] Analecta Bollandiana 
\item[AnalP-long] Analecta papyrologica 
\item[AnalRom-long] Analecta Romana Instituti Danici 
\item[AnArqAnd-long] Anuario arqueológico de Andalucía 
\item[Anas-long] Anas. Museo nacional de arte romano de Mérida 
\item[AnatA-long] Anatolian Archaeology. Reports on Research Conducted in Turkey 
\item[Anatolia-long] Anatolia. Revue annuelle de l’Institut d’archéologie de l’Université d’Ankara 
\item[ANaturwiss-long] Archäologie und Naturwissenschaften 
\item[AncCivScytSib-long] Ancient Civilizations from Scythia to Siberia. An International Journal of Comparative Studies in History and Archaeology 
\item[AncHistB-long] The Ancient History Bulletin 
\item[AncInd-long] The Ancient India 
\item[AncNearEastSt-long] Ancient Near Eastern Studies. An Annual 
\item[AnCord-long] Anales de arqueología cordobesa 
\item[AncSoc-long] Ancient Society 
\item[AncW-long] The Ancient World 
\item[AncWestEast-long] Ancient West and East 
\item[AnDubr-long] Annali Zavoda za povijesne znanosti Istraivakog centra Jugoslavenske akademije znanosti i umjetnosti u Dubrovniku 
\item[ANews-long] Archaeological News 
\item[ANilMoy-long] Archéologie du Nil moyen 
\item[ANL-long] The Archaeological News Letter 
\item[AnMunFaro-long] Anais do municípo de Faro 
\item[AnMurcia-long] Anales de prehistoria y arqueología. Universidad de Murcia 
\item[AnnAcEtr-long] Annuario. Accademia etrusca di Cortona 
\item[AnnAcTorino-long] Annuario della Accademia delle scienze di Torino 
\item[AnnAStorAnt-long] Annali. Sezione di archeologia e storia antica. Istituto universitario orientale di Napoli. Dipartimento di studi del mondo classico e del Mediterraneo antico 
\item[AnnBari-long] Annali della Facoltà di lettere e filosofia, Università degli Studi, Bari 
\item[AnnBenac-long] Annali Benacensi 
\item[AnnBiblAModena-long] Annuario bibliografico di archeologia. Modena 
\item[AnnBiblARom-long] Annuario bibliografico di archeologia. Nuove accessioni del \ldots. Biblioteca dell’Istituto nazionale di archeologia e storia dell’arte, Roma 
\item[AnnByzConf-long] Annual Byzantine Studies Conference. Abstracts of Papers 
\item[AnnCagl-long] Annnali della Facoltà di lettere e filosofia dell'Università di Cagliari 
\item[AnnCaglMag-long] Annali della Facoltà di magistero dell'Università di Cagliari 
\item[AnnEconSocCiv-long] Annales. Economies, sociétés, civilisations 
\item[AnnEgBibl-long] Annual Egyptological Bibliography 
\item[AnnEth-long] Annales d'Éthiopie 
\item[AnnFaina-long] Annali della Fondazione per il Museo Claudio Faina 
\item[AnnHistA-long] Annales d'histoire et d'archéologie 
\item[AnnHistScSoc-long] Annales. Histoire, sciences sociales 
\item[AnnIstGiapp-long] Annuario. Istituto giapponese di cultura in Roma 
\item[AnnIstItNum-long] Annali. Istituto italiano di numismatica 
\item[AnnLecce-long] Annali dell'Università di Lecce. Facoltà di lettere e filosofia e di magistero 
\item[AnnLeedsUnOrSoc-long] The Annual of Leeds University Oriental Society 
\item[AnnMacerata-long] Annali della Facoltà di lettere e filosofia, Università di Macerata 
\item[AnnMessMag-long] Nuovi annali della Facoltà di magistero dell'Università di Messina 
\item[AnnMusRov-long] Annali del Museo civico di Rovereto. Sezione archeologia, storia, scienze naturali 
\item[AnnNap-long] Annali della Facoltà di lettere e filosofia, Università di Napoli 
\item[AnnNivern-long] Les annales des pays Nivernais 
\item[AnnNoment-long] Annali. Associazione nomentana di storia e archeologia 
\item[AnnOrNap-long] Annali. Rivista del Dipartimento di studi asiatici e del Dipartimento di studi e ricerche su Africa e paesi arabi, Istituto universitario orientale di Napoli 
\item[AnnotNum-long] Annotazioni numismatiche 
\item[AnnPerugia-long] Annali della Facoltà di lettere e filosofia, Università degli studi di Perugia, 1. Studi classici 
\item[AnnPisa-long] Annali della Scuola normale superiore di Pisa 
\item[AnnPontAcRom-long] Annuario della Pontificia accademia romana di archeologia 
\item[AnnRepBSA-long] Annual Report of Council. British School of Archaeology at Athens 
\item[AnnRepCypr-long] Annual Report of the Department of Antiquities, Republic of Cyprus 
\item[AnnRepFoggArtMus-long] The Annual Report of the Fogg Art Museum 
\item[AnnSiena-long] Annali della Facoltà di lettere e filosofia, Università di Siena 
\item[AnnuarioAcLinc-long] Annuario della Accademia nazionale dei Lincei 
\item[AnnuarioLecce-long] Annuario. Liceo-ginnasio statale G. Palmieri, Lecce 
\item[AnnUnBud-long] Annales Universitatis scientiarum Budapestinensis de Rolando Eötvös nominatae 
\item[AnnWorcArtMus-long] Annual (Report). Worcester Art Museum 
\item[Anodos-long] Anodos. Studies of Ancient World 
\item[AnOr-long] Analecta orientalia. Commentationes scientificae de rebus orientis antiqui 
\item[ANRW-long] Aufstieg und Niedergang der römischen Welt 
\item[Anschnitt-long] Der Anschnitt. Mitteilungsblatt der Vereinigung der Freunde von Kunst und Kultur im Bergbau 
\item[ANSMusNotes-long] Museum Notes. American Numismatic Society 
\item[AnSt-long] Anatolian Studies 
\item[Antaeus-long] Antaeus. Communicationes ex Instituto archaeologico Academiae scientiarum hungaricae 
\item[AntAfr-long] Antiquités africaines 
\item[AntChr-long] Antike und Christentum 
\item[AntCl-long] L'antiquité classique 
\item[AnthrAChron-long] Ανθρωπολογικά και Αρχαιολογικά Χρονικά 
\item[Anthropos-long] Άνθρωπος. Όργανο της Ανθρωπολογικής Εταιρείας Ελλάδος 
\item[Antichthon-long] Antichthon. Journal of the Australian Society for Classical Studies 
\item[AntigCr-long] Antigüedad y cristianismo. Monografías históricas sobre la antigüedad tardía 
\item[Antipolis-long] Antipolis. A Journal of Mediterranean Archaeology 
\item[Antiqua-long] Antiqua. Rivista dell'Archeoclub d'Italia 
\item[Antiquity-long] Antiquity. A Quarterly Review of Archaeology 
\item[AntJ-long] The Antiquaries Journal 
\item[AntK-long] Antike Kunst 
\item[AntNat-long] Antiquités nationales. Saint-Germain-en-Laye 
\item[AntPisa-long] Antichità pisane 
\item[AntPl-long] Antike Plastik 
\item[AntSurv-long] Antiquity and Survival 
\item[AntTard-long] Antiquité tardive. Revue internationale d'histoire et d'archéologie 
\item[AnzAW-long] Anzeiger für die Altertumswissenschaft 
\item[AnzWien-long] Anzeiger. Österreichische Akademie der Wissenschaften, Philosophisch-Historische Klasse 
\item[AOAT-long] Alter Orient und Altes Testament. Veröffentlichungen zur Kultur und Geschichte des Alten Orients und des Alten Testaments 
\item[AoF-long] Altorientalische Forschungen 
\item[AOtkryt-long] Archeologičeskie otkrytija 
\item[APamKiiv-long] Archeologični pamjatki URSR 
\item[APh-long] L'année philologique 
\item[APol-long] Archaeologia Polona 
\item[Apollo-long] Apollo. Bolletino dei musei provinciali del Salernitano 
\item[ApolloLond-long] Apollo. The International Magazine of the Arts 
\item[APort-long] O arqueólogo português 
\item[AppRomFil-long] Appunti romani di filologia. Studi e comunicazioni di filologia, linguistica e letteratura greca e latina 
\item[APregl-long] Arheološki pregled. Arheološko društvo Jugoslavije 
\item[Apulum-long] Apulum. Acta Musei Apulensis 
\item[AquiLeg-long] Aquila legionis. Cuadernos des estudios sobre el ejército romano 
\item[AquilNost-long] Aquileia nostra. Bollettino dell'Associazione nazionale per Aquileia 
\item[Aquitania-long] Aquitania. Une revue inter-régionale d'archéologie 
\item[ArabAEpigr-long] Arabian Archaeology and Epigraphy 
\item[ARadRaspr-long] Arheolokiradovi i rasprave 
\item[ArbFBerSaechs-long] Arbeits- und Forschungsberichte zur sächsischen Bodendenkmalpflege 
\item[Archaeographie-long] Archäographie. Archäologie und elektronische Datenverarbeitung %*Abweichung!
\item[Archaeologia-long] Archaeologia or Miscellaneous Tracts Relating to Antiquity Published by the Society of Antiquaries of London 
\item[Archaeology-long] Archaeology. A Magazine Dealing with the Antiquity of the World 
\item[Archaeometry-long] Archaeometry. Bulletin of the Research Laboratory for Archaeology and History of Art, Oxford University 
\item[Archaiognosia-long] Αρχαιογνωσία 
\item[ArchBegriffsGesch-long] Archiv für Begriffsgeschichte 
\item[ArchByzMnem-long] Αρχείον των Βυζαντινών Μνημείων της Ελλάδος  
\item[ArchCl-long] Archeologia classica 
\item[Archeo-long] Archeo. Attualità del passato 
\item[ArcheogrTriest-long] Archeografo triestino 
\item[ArcheologiaParis-long] Archeologia, Paris. L'archéologie dans le monde et tout ce qui concerne les recherches historiques, artistiques et scientifiques sur terre et dans les mers 
\item[ArcheologiaRoma-long] Archeologia. Rivista bimestrale. Roma 
\item[ArcheologiaWarsz-long] Archeologia. Rocznik Instytutu archeologii i etnologii, Polskiej akademii nauk 
\item[ArcheologijaKiiv-long] Archeologija. Nacional'na akademija nauk Ukraini. Institut archeologii 
\item[ArcheologijaSof-long] Archeologija. Organ na Archeologičeskija institut i muzej (pri Bălgarskata akademii nauk) 
\item[ArchEubMel-long] Αρχείον Ευβοϊκών Μελετών 
\item[ArchHom-long] Archaeologia Homerica 
\item[Architectura-long] Architectura. Zeitschrift für Geschichte der Baukunst 
\item[Archivi-long] Archivi. Archivi d'Italia e rassegna internazionale degli archivi 
\item[ArchPF-long] Archiv für Papyrusforschung und verwandte Gebiete 
\item[ArchPrehistLev-long] Archivo de prehistoria levantina 
\item[ArchRel-long] Archiv für Religionsgeschichte 
\item[ArchStorCal-long] Archivio storico per la Calabria e la Lucania 
\item[ArchStorPugl-long] Archivio storico pugliese 
\item[ArchStorRom-long] Archivio della Società romana di storia patria 
\item[ArchStorSicOr-long] Archivio storico per la Sicilia orientale 
\item[ArchStorSir-long] Archivio storico siracusano 
\item[Arctos-long] Arctos. Acta philologica Fennica 
\item[ARepLond-long] Archaeological Reports 
\item[Argo-long] Argo. časopis slovenskih muzejev, Narodni Muzej Slovenije 
\item[ArOr-long] Archív orientální. Quarterly Journal of African and Asian Studies 
\item[ArOrMono-long] Archív orientální. Quarterly Journal of African, Asian and Latin American Studies. Monografie Archívu orientálního 
\item[ArOrSuppl-long] Archív orientální. Quarterly Journal of African, Asian and Latin American Studies. Supplementa 
\item[ARozhl-long] Archeologické rozhledy 
\item[ArqBeja-long] Arquivo de Beja. Boletim, estudos, arquivo 
\item[Arse-long] Arse. Boletín del Centro arqueológico saguntino 
\item[ArsGeorg-long] Ars Georgica 
\item[ArtAntMod-long] Arte antica e moderna 
\item[ArtARhone-long] Art et archéologie en Rhône-Alpes %*Abweichung!
\item[ArtAs-long] Artibus Asiae 
\item[ArtB-long] The Art Bulletin 
\item[ArtJ-long] Art Journal 
\item[ArtLomb-long] Arte lombarda 
\item[ArtMediev-long] Arte medievale 
\item[ArtVirg-long] Arts in Virginia 
\item[ARV2-long] J. D. Beazley, Attic Red-figure Vase-painters \textsuperscript{2}(Oxford 1963) 
\item[ASachs-long] Archäologie in Sachsen-Anhalt 
\item[ASAE-long] Annales du Service des antiquités de l’Égypte 
\item[ASammlUnZuerch-long] Archäologische Sammlung der Universität Zürich %*Abweichung!
\item[ASAtene-long] Annuario della Scuola archeologica di Atene e delle missioni italiane in Oriente 
\item[ASbor-long] Archeologičeskij sbornik. Gosudarstvennyj ordena Lenina Ermitaž 
\item[ASchw-long] Archäologie der Schweiz. Mitteilungsblatt der Schweizerischen Gesellschaft für Ur- und Frühgeschichte 
\item[ASoc-long] Archeologia e società 
\item[ASoloth-long] Archäologie des Kantons Solothurn 
\item[ASR-long] Die antiken Sarkophagreliefs 
\item[Assaph-long] Assaph. Studies in Art History 
\item[AssyrMisc-long] Assyriological Miscellanies 
\item[AST-long] AratirmaSonuçlariToplantisi 
\item[ASub-long] L'archeologo subacqueo. Quadrimestrale di archeologia subacquea e navale 
\item[ASubacq-long] Archeologia subacquea. Studi, ricerche e documenti 
\item[Athenaeum-long] Athenaeum. Studi di letteratura e storia dell'antichità 
\item[Atiqot-long] `Atiqot. Journal of the Israel Department of Antiquities 
\item[AtiqotHeb-long] `Atiqot. Journal of the Israel Department of Antiquities. Hebrew Series 
\item[Atlal-long] Atlal. The Journal of Saudi Arabian Archaeology 
\item[AttiAcPontan-long] Atti della Accademia pontaniana 
\item[AttiAcRov-long] Atti della Accademia Roveretana degli Agiati. Contributi della classe di scienze umane, di lettere ed arti 
\item[AttiAcTorino-long] Atti della Accademia delle scienze di Torino, 2. Classe di scienze morali, storiche e filologiche 
\item[AttiCAntCl-long] Atti. Centro ricerche e documentazione sull'antichità classica 
\item[AttiCItRom-long] Atti. Centro studi e documentazione sull'Italia romana 
\item[AttiMemBologna-long] Atti e memorie. Deputazione di storia patria per le province di Romagna 
\item[AttiMemDal-long] Atti e memorie della Società dalmata di storia patria 
\item[AttiMemFirenze-long] Atti e memorie dell'Academia toscana di scienze e lettere »La Columbaria« 
\item[AttiMemIstria-long] Atti e memorie della Società istriana di archeologia e storia patria 
\item[AttiMemMagnaGr-long] Atti e memorie della Società Magna Grecia 
\item[AttiMemModena-long] Atti e memorie. Deputazione di storia patria per le antiche provincie modenesi 
\item[AttiMemTivoli-long] Atti e memorie della Società tiburtina di storia e d'arte 
\item[AttiMusTrieste-long] Atti dei Civici musei di storia ed arte di Trieste 
\item[AttiPalermo-long] Atti della Accademia di scienze, lettere e arti di Palermo 
\item[AttiRovigno-long] Atti. Centro di ricerche storiche, Rovigno 
\item[AttiSocFriuli-long] Atti della Società per la preistoria e protostoria della regione Friuli -- Venezia Giulia 
\item[AttiVenezia-long] Atti. Istituto veneto di scienze, lettere ed arti 
\item[AuA-long] Antike und Abendland 
\item[AulaOr-long] Aula orientalis. Revista de estudios del Próximo Oriente antiguo 
\item[AusgrFu-long] Ausgrabungen und Funde. Nachrichtenblatt der Landesarchäologie 
\item[AusgrFuWestf-long] Ausgrabungen und Funde in Westfalen-Lippe 
\item[AustrRom-long] Pro Austria Romana 
\item[AUTerr-long] Archeologia, uomo, territorio. Rivista dei Gruppi archeologici Nord Italia 
\item[AUWE-long] Ausgrabungen in Uruk-Warka. Endberichte 
\item[AV-long] Archäologische Veröffentlichungen. Deutsches Archäologisches Institut, Abteilung Kairo 
\item[AVen-long] Archeologia veneta 
\item[AVes-long] Arheološki vestnik (Ljubljana) 
\item[AViva-long] Archeologia viva 
\item[AvP-long] Altertümer von Pergamon 
\item[AW-long] Antike Welt. Zeitschrift für Archäologie und Kulturgeschichte 
\item[AyasofyaMuezYil-long] Ayasofia Müzesi yıllığı. Annual of Ayasofya Museum \label{AyasofyaMuezYil-lang} %*Abweichung!
\item[AZ-long] Archäologische Zeitung 
\item[Azotea-long] Azotea. Revista de cultura del Ayuntamiento de Coria del Río 
\item[BA-long] Bollettino di archeologia 
\item[Baalbek-long] Baalbek. Ergebnisse der Ausgrabungen und Untersuchungen in den Jahren 1898 bis 1905 
\item[BAAlger-long] Bulletin d'archéologie algérienne 
\item[BABarcel-long] Butlletí informatiu de l'Institut de prehistòria i arqueologia de la Diputació provincial de Barcelona 
\item[BABesch-long] Bulletin antieke beschaving. Annual Papers on Classical Archaeology 
\item[BAcRHist-long] Boletín de la Real academia de la historia 
\item[BACopt-long] Bulletin de la Société d'archéologie copte 
\item[BadFuBer-long] Badische Fundberichte 
\item[Baetica-long] Baetica. Estudios de arte, geografía e historia 
\item[BaF-long] Baghdader Forschungen 
\item[BalacaiKoez-long] Balácai közlemények %*Abweichung!
\item[BalkSt-long] Balkan Studies 
\item[BALond-long] Bulletin of the Institute of Archaeology, University of London 
\item[BALux-long] Bulletin d'archéologie luxembourgeoise 
\item[BaM-long] Baghdader Mitteilungen 
\item[BAMaroc-long] Bulletin d'archéologie marocaine 
\item[BAmSocP-long] The Bulletin of the American Society of Papyrologists 
\item[BAncOrMus-long] Bulletin of the Ancient Orient Museum (Tokyo) 
\item[BAngers-long] Bulletin du Centre de recherches et d'enseignement de l'antiquité, Angers 
\item[BAngloIsrASoc-long] Bulletin of the Anglo-Israel Archaeological Society 
\item[BAnnMusFerr-long] Bollettino annuale. Musei ferraresi 
\item[BAntFr-long] Bulletin de la Société nationale des antiquaires de France 
\item[BAntLux-long] Bulletin des antiquités luxembourgeoises 
\item[BAParis-long] Bulletin archéologique du Comité des travaux historiques et scientifiques. Antiquités nationales 
\item[BAProv-long] Bulletin archéologique de Provence 
\item[BAR-long] British Archaeological Reports. British Series 
\item[BArchAlex-long] Bulletin. Société archéologique d'Alexandrie 
\item[BArchit-long] Bollettino del Centro di studi per la storia dell'architettura 
\item[BARIntSer-long] British Archaeological Reports. International Series 
\item[BASard-long] Nuovo bullettino archeologico sardo 
\item[BAsEspA-long] Boletín. Asociación española de amigos de la arqueología 
\item[BAsInst-long] Bulletin of the Asia Institute 
\item[BASOR-long] Bulletin of the American Schools of Oriental Research 
\item[BAssBude-long] Bulletin de l'Association Guillaume Budé %*Abweichung!
\item[BAssMosAnt-long] Bulletin d'information de l'Association internationale pour l'étude de la mosaïque antique 
\item[BASub-long] Bollettino di archeologia subacquea 
\item[BASudEstEur-long] Bulletin d'archéologie sud-est européenne 
\item[BATarr-long] Bulletí arqueològic. Reial societat arqueològica tarraconense. Boletín arqueológico. Real sociedad arqueológica tarragonese 
\item[BAur-long] Boletín auriense 
\item[BAVA-long] Beiträge zur Allgemeinen und Vergleichenden Archäologie 
\item[BayVgBl-long] Bayerische Vorgeschichtsblätter 
\item[BBasil-long] Bollettino storico della Basilicata 
\item[BBelgRom-long] Bulletin de l'Institut historique belge de Rome 
\item[BBolsena-long] Bollettino di studi e ricerche. Biblioteca comunale di Bolsena 
\item[BBrByzSt-long] Bulletin of British Byzantine Studies 
\item[BCamuno-long] Bullettino del Centro Camuno di studi preistorici 
\item[BCASic-long] Beni culturali e ambientali. Sicilia 
\item[BCercleNum-long] Bulletin du Cercle d'études numismatiques 
\item[BCH-long] Bulletin de correspondance hellénique 
\item[BCircNumNap-long] Bollettino del Circolo numismatico napoletano 
\item[BCl-long] Bollettino dei classici 
\item[BClevMus-long] The Bulletin of The Cleveland Museum of Art 
\item[BCom-long] Bullettino della Commissione archeologica comunale di Roma 
\item[BCord-long] Bulletin d'information de l'Association internationale pour l'étude de la mosaïque antique 
\item[BdA-long] Bollettino d'arte 
\item[BdE-long] Bibliothèque d'études, Institut français d'archéologie orientale, Kairo 
\item[BdEC-long] Bibliothèque d'études coptes, Institut français d'archéologie orientale, Kairo 
\item[BdI-long] Bullettino dell'Instituto di corrispondenza archeologica 
\item[BDirRom-long] Bullettino dell'Istituto di diritto romano »Vittorio Scialoja« 
\item[BeazleyAddenda2-long] T. H. Carpenter (Hrsg.), Beazley Addenda \textsuperscript{2}(Oxford 1989) %*Abweichung!
\item[BeazleyPara-long] J. D. Beazley, Paralipomena. Additions to Attic Black-figure Vase-painters and to Attic Red-figure Vase-painters (Oxford 1971) %*Abweichung!
\item[BEcAntNimes-long] Bulletin (annuel) de l'École antique de Nîmes %*Abweichung!
\item[BediKart-long] Bedi Kartlisa. Revue de kartvélologie 
\item[BEFAR-long] Bibliothèque des Écoles françaises d'Athènes et de Rome 
\item[BeitrESkAr-long] Beiträge zur Erschließung hellenistischer und kaiserzeitlicher Skulptur und Architektur 
\item[BeitrNamF-long] Beiträge zur Namenforschung 
\item[BeitrSudanF-long] Beiträge zur Sudanforschung 
\item[BelArt-long] Bellas artes (Madrid) 
\item[Belleten-long] Belleten. Türk Tarih Kurumu 
\item[Benacus-long] Benàcus. Museo archeologico della Val Tenesi 
\item[BerBayDenkmPfl-long] Bericht der Bayerischen Bodendenkmalpflege 
\item[BerDFG-long] Bericht der Deutschen Forschungsgemeinschaft 
\item[BerlBeitrArchaeom-long] Berliner Beiträge zur Archäometrie %*Abweichung!
\item[BerlBlVFruehGesch-long] Berliner Blätter für Vor- und Frühgeschichte %*Abweichung!
\item[BerlJbVFruehGesch-long] Berliner Jahrbuch für Vor- und Frühgeschichte %*Abweichung!
\item[BerlMus-long] Berliner Museen 
\item[BerlNumZ-long] Berliner numismatische Zeitschrift 
\item[BerOudhBod-long] Berichten van de Rijksdienst voor het oudheidkundig bodemonderzoek 
\item[BerRGK-long] Bericht der Römisch-Germanischen Kommission 
\item[BerVerhLeipz-long] Berichte über die Verhandlungen der Sächsischen Akademie der Wissenschaften zu Leipzig 
\item[Berytus-long] Berytus. Archaeological Studies 
\item[BEspA-long] Boletín. Asociación española de amigos de la arqueología 
\item[BEspOr-long] Boletín de la Asociación española de orientalistas 
\item[BEtOr-long] Bulletin d'études orientales 
\item[BFilGrPadova-long] Bollettino dell'Istituto di filologia greca, Università di Padova 
\item[BFilLingSic-long] Bollettino. Centro di studi filologici e linguistici siciliani 
\item[BFlegr-long] Bollettino flegreo. Rivista di storia, arte e scienze 
\item[BFoligno-long] Bollettino storico della città di Foligno 
\item[BHarvMus-long] Harvard University Art Museums Bulletin 
\item[BIasos-long] Bollettino dell'Associazione Iasos di Caria 
\item[BibAr-long] The Biblical Archaeologist. The American School of Oriental Research New Haven 
\item[BiblClOr-long] Bibliotheca classica orientalis 
\item[BiblSymb-long] Bibliographie zur Symbolik, Ikonographie und Mythologie. Internationales Referateorgan 
\item[BIBulg-long] Izvestija na Archeologičeskija institut. Bulletin de l’Institut d’archéologie 
\item[BICS-long] Bulletin of the Institute of Classical Studies of the University of London 
\item[BIFAO-long] Bulletin de l'Institut français d'archéologie orientale 
\item[BInfCentumcellae-long] Bollettino di informazioni. Associazione archeologica Centumcellae 
\item[BInfCESDAE-long] Bollettino di informazioni del Centro di studi e documentazione sull'area elima 
\item[BiogrZbor-long] Biogradski zbornik 
\item[BiOr-long] Bibliotheca orientalis 
\item[BIstOrvieto-long] Bollettino dell'Istituto storico artistico orvietano 
\item[BJaen-long] Boletín del Instituto de estudios giennenses %*Abweichung!
\item[BJb-long] Bonner Jahrbücher des Rheinischen Landesmuseums in Bonn 
\item[BJerus-long] Bulletin. The Hebrew University, Jerusalem, Rabinowitz Fund 
\item[BLaborMusLouvre-long] Bulletin du laboratoire du Musée du Louvre 
\item[BLazioMerid-long] Bollettino dell'Istituto di storia e di arte del Lazio meridionale 
\item[BLikUm-long] Bulletin Razreda za likovne umjetnosti Hrvatske akademije znanosti i umjetnosti 
\item[BlMueFreundeF-long] Blätter für Münzfreunde und Münzforschung %*Abweichung!
\item[BLugo-long] Boletín de la Comisión provincial de monumentos históricos y artísticos de Lugo 
\item[BMCGreekCoins-long] Catalogue of the Greek Coins in the British Museums %*Abweichung!
\item[BMCOR-long] Catalogue of Oriental Coins in the British Museum I--X 
\item[BMCRE-long] H. Mattingly (u. a.), Coins of the Roman Empire in the British Museum (London 1923--1950; \textsuperscript{2}1975) 
\item[BMCRRI-III-long] H. A. Grueber, Coins of the Roman Republic in the British Museum I--III (London 1910) %*Abweichung!
\item[BMetrMus-long] The Metropolitan Museum of Art Bulletin 
\item[BMon-long] Bulletin monumental 
\item[BMonMusPont-long] Bollettino. Monumenti, musei e gallerie pontificie 
\item[BMQ-long] The British Museum Quarterly 
\item[BMQNSuppl-long] The British Museum Quarterly. News Supplement 
\item[BMusBeyrouth-long] Bulletin du Musée de Beyrouth 
\item[BMusBrux-long] Bulletin des Musées royaux d'art et d'histoire, Bruxelles 
\item[BMusCadiz-long] Boletín del Museo de Cádiz 
\item[BMusCivRom-long] Bullettino del Museo della civiltà romana 
\item[BMusFA-long] Bulletin. Museum of Fine Arts, Boston 
\item[BMusHongr-long] Bulletin du Musée hongrois des beaux-arts 
\item[BMusMadr-long] Boletín del Museo arqueológico nacional, Madrid 
\item[BMusMich-long] Bulletin. Museums of Art and Archaeology, University of Michigan 
\item[BMusMonaco-long] Bulletin du Musée d'anthropologie préhistorique de Monaco 
\item[BMusPadova-long] Bollettino del Museo civico di Padova 
\item[BMusPBelArt-long] Boletín del Museo provincial de bellas artes 
\item[BMusRom-long] Bollettino dei Musei comunali di Roma 
\item[BMusVars-long] Bulletin du Musée national de Varsovie 
\item[BMusZaragoza-long] Museo de Zaragoza. Boletín 
\item[BNumParis-long] Bulletin de la Société française de numismatique 
\item[BNumRoma-long] Bollettino di numismatica 
\item[Bogazkoey-Hattusa-long] Boğazköy-Hattuša. Ergebnisse der Ausgrabungen %*Abweichung!
\item[Bolskan-long] Bolskan. Revista de arqueología del Instituto de estudios Altoaragoneses, revista de arqueología Oscense 
\item[BonnHVg-long] Bonner Hefte zur Vorgeschichte 
\item[BOntMus-long] Bulletin of the Royal Ontario Museum of Archaeology, University of Toronto 
\item[Boreas-long] Boreas. Münstersche Beiträge zur Archäologie 
\item[BoreasUpps-long] Boreas. Uppsala Studies in Ancient Mediterranean and Near Eastern Civilization 
\item[BPeintRom-long] Bulletin de liaison. Centre d'études des peintures murales romaines 
\item[BPI-long] Bullettino di paletnologia italiana 
\item[BPrehistAlp-long] Bulletin d'études préhistoriques alpines %*Abweichung!
\item[BProAvent-long] Bulletin de l'Association Pro Aventico 
\item[BProvidence-long] Bulletin of the Rhode Island School of Design. Museum Notes 
\item[BracAug-long] Bracara Augusta. Revista cultural da Câmara municipal de Braga 
\item[BracaraAugusta-long] Bracara Augusta. Revista cultural da Câmara municipal de Braga 
\item[BremABl-long] Bremer archäologische Blätter 
\item[BRest-long] Bollettino dell'Istituto centrale del restauro 
\item[Brigantium-long] Brigantium. Museo arqueolóxico e histórico 
\item[BrMusYearbook-long] The British Museum Yearbook 
\item[BSA-long] The Annual of the British School at Athens 
\item[BSAA-long] Boletín del Seminario de estudios de arte y arqueología, Universidad de Valladolid 
\item[BSFE-long] Bulletin de la Société française d'égyptologie 
\item[BSiena-long] Bullettino senese di storia patria 
\item[BSOAS-long] Bulletin of the School of Oriental and African Studies (London) 
\item[BSocAChamp-long] Bulletin de la Société archéologique champenoise 
\item[BSocBiblReinach-long] Bulletin de liaison de la Société des amis de la Bibliothèque Salomon Reinach 
\item[BSocNumRom-long] Buletinul Societăţii numismatice române 
\item[BSR-long] Papers of the British School at Rome 
\item[BStLat-long] Bollettino di studi latini 
\item[BStorArt-long] Bollettino della Unione storia ed arte 
\item[BTextilAnc-long] Bulletin du Centre international d'étude des textiles anciens 
\item[BTorino-long] Bollettino della Società piemontese di archeologia e belle arti 
\item[BTravTun-long] Bulletin des travaux de l'Institut national du patrimoine. Comptes rendus 
\item[BudReg-long] Budapest régiségei 
\item[BulletinGetty-long] Bulletin. J. Paul Getty Museum of Art 
\item[BulletinNorthampton-long] Bulletin. Smith College Museum of Art 
\item[BVallad-long] Boletín del Seminario de estudios de arte y arqueología, Universidad de Valladolid 
\item[BVitoria-long] Boletín de la Institución »Sancho el Sabio« 
\item[BWaltersArtGal-long] The Walters Art Gallery Bulletin 
\item[BWPr-long] Winckelmannsprogramm der Archäologischen Gesellschaft zu Berlin 
\item[Byzantina-long] Βυζαντινά. Επιστημονικόν Όργανον Κέντρου Βυζαντινών Ερευνών Φιλοσοφικής Σχολής Αριστοτελείου Πανεπιστημίου Θεσσαλονίκης
\item[ByzF-long] Byzantinische Forschungen. Internationale Zeitschrift für Byzantinistik 
\item[ByzJb-long] Byzantinisch-neugriechische Jahrbücher 
\item[ByzZ-long] Byzantinische Zeitschrift 
\item[BZ-long] Biblische Zeitschrift 
\item[CAA-long] Corpus antiquitatum Aegyptiacarum 
\item[CAD-long] The Assyrian Dictionary of the Oriental Institute of the University of Chicago 
\item[CadA-long] Cadernos de arqueologia 
\item[Caesaraugusta-long] Caesaraugusta. Publicaciones del Seminario de Arqueología y Numismática Aragonesas 
\item[Caesarodunum-long] Caesarodunum. Bulletin de l'Institut d'études latines et du Centre de recherches A. Piganiol 
\item[CAH-long] The Cambridge Ancient History 
\item[CahArmeeRom-long] Cahiers du Groupe de recherches sur l'armée romaine et les provinces 
\item[CahASubaqu-long] Cahiers d'archéologie subaquatique 
\item[CahByrsa-long] Cahiers de Byrsa 
\item[CahCEC-long] Cahier. Centre d'études chypriotes 
\item[CahCerEg-long] Cahiers de la céramique égyptienne 
\item[CahDelFrIran-long] Cahiers de la Délégation française en Iran 
\item[CahGlotz-long] Cahiers du Centre Gustave-Glotz. Revue reconnue par le CNRS 
\item[CahKarnak-long] Cahiers de Karnak 
\item[CahLig-long] Cahiers ligures de préhistoire et de protohistoire 
\item[CahMariemont-long] Les cahiers de Mariemont. Bulletin du Musée royal de Mariemont 
\item[CahMusChampollion-long] Cahiers du Musée Champollion. Histoire et archéologie 
\item[CahPEg-long] Cahiers de recherches de l'Institut de papyrologie et d'égyptologie de Lille. Sociétés urbaines en Égypte et au Soudan 
\item[CahRhod-long] Cahiers rhodaniens 
\item[CahTun-long] Cahiers de Tunisie 
\item[CalifStClAnt-long] California Studies in Classical Antiquity 
\item[CambrAJ-long] Cambridge Archaeological Journal 
\item[CArch-long] Cahiers archéologiques 
\item[CarinthiaI-long] Carinthia I. Geschichtliche und volkskundliche Beiträge zur Heimatkunde Kärntens %*Abweichung!
\item[CarnuntumJb-long] Carnuntum-Jahrbuch. Zeitschrift für Archäologie und Kulturgeschichte des Donauraumes 
\item[Carpica-long] CarpicaMuzeuljudeeandeistorieiartBacu 
\item[Carrobbio-long] Il Carrobbio. Rivista di studi bolognesi 
\item[CAT-long] Ch. W. Clairmont, Classical Attic Tombstones (Kilchberg 1993--1995) 
\item[CE-long] Cuadernos emeritenses 
\item[CEDAC-long] CEDAC. Bulletin. Centre d'études et de documentation archéologique de la conservation de Cartage 
\item[CEFR-long] Collection de l'École française de Rome 
\item[Celticum-long] Celticum. Supplément à Ogam 
\item[CercA-long] Cercetriarheologice 
\item[CercNum-long] Cercetări numismatice. Muzeul naţional de istorie 
\item[Chiron-long] Chiron. Mitteilungen der Kommission für Alte Geschichte und Epigraphik des Deutschen Archäologischen Instituts 
\item[ChronEg-long] Chronique d'Égypte 
\item[CIA-long] Corpus inscriptionum Atticarum 
\item[CIE-long] Corpus inscriptionum Etruscarum 
\item[CIG-long] Corpus inscriptionum Graecarum 
\item[CIH-long] Corpus inscriptionum Semiticarum. Pars quarta. Inscriptiones himyariticas et sabaeas continens 
\item[CIL-long] Corpus inscriptionum Latinarum 
\item[CincArtB-long] The Cincinnati Art Museum Bulletin 
\item[CIS-long] Corpus inscriptionum Semiticarum 
\item[CIstAMilano-long] Contributi dell'Istituto di archeologia. Pubblicazioni dell'Università cattolica del Sacro Cuore, Milano 
\item[CivClCr-long] Civiltà classica e cristiana 
\item[CivPad-long] Civiltà padana. Archeologia e storia del territorio 
\item[ClAnt-long] Classical Antiquity 
\item[ClevStHistArt-long] Cleveland Studies in the History of Art 
\item[Clio-long] Clio. Revista do Centro de história da Universidade Lisboa 
\item[ClIre-long] Classics Ireland 
\item[ClJ-long] The Classical Journal 
\item[ClMediaev-long] Classica et mediaevalia. Revue danoise de philologie et d'histoire 
\item[ClPhil-long] Classical Philology 
\item[ClQ-long] The Classical Quarterly 
\item[ClR-long] The Classical Review 
\item[ClRh-long] Clara Rhodos 
\item[CMatAOr-long] Contributi e materiali di archeologia orientale 
\item[CMGr-long] Convegni di studi sulla Magna Grecia 
\item[CMS-long] Corpus der minoischen und mykenischen Siegel 
\item[CoinHoards-long] Coin Hoards. The Royal Numismatic Society, London %*Abweichung!
\item[ColloquiSod-long] Colloqui del Sodalizio 
\item[CommunicAHung-long] Communicationes archaeologicae hungaricae 
\item[Complutum-long] Complutum. Publicaciones del Departamento de prehistoria de la Universidad complutense de Madrid 
\item[Conoscenze-long] Conoscenze. Rivista annuale della Soprintendenza archeologica e per i beni ambientali, architettonici, artistici e storici del Molise 
\item[Corduba-long] Corduba archaeologica 
\item[Corinth-long] Corinth. Results of Excavations Conducted by the American School of Classical Studies at Athens 
\item[CRAI-long] Académie des inscriptions et belles-lettres. Comptes rendus des séances de l'Académie 
\item[CretAnt-long] Creta antica. Rivista annuale di studi archeologici, storici ed epigrafici 
\item[CretSt-long] Cretan Studies 
\item[CronA-long] Cronache di archeologia 
\item[CronErcol-long] Cronache ercolanesi. Bollettino del Centro internazionale per lo studio dei papiri ercolanesi 
\item[CronPomp-long] Cronache pompeiane 
\item[CRPetersbourg-long] Compte-rendu de la Commission impériale archéologique, St. Pétersbourg %*Abweichung!
\item[CSE-long] Corpus speculorum Etruscorum 
\item[CSIR-long] Corpus signorum Imperii Romani 
\item[CSSpecPisa-long] Contributi della Scuola di specializzazione in archeologia dell'Università degli studi di Pisa 
\item[CuadAMed-long] Cuadernos de arqueología mediterránea 
\item[CuadArquitRom-long] Cuadernos de arquitectura romana 
\item[CuadCastellon-long] Cuadernos de prehistoria y arqueología castellonense 
\item[CuadCat-long] Cuaderni catanesi di studi classici e medievali 
\item[CuadFilCl-long] Cuadernos de filología clásica. Facultad de letras y filosofía, Universidad de Madrid 
\item[CuadGallegos-long] Cuadernos de estudios gallegos 
\item[CuadGranada-long] Cuadernos de prehistoria de la Universidad de Granada 
\item[CuadNavarra-long] Cuadernos de arqueología de la Universidad de Navarra 
\item[CuadPrehistA-long] Cuadernos de prehistoria y arqueología. Universidad autónoma de Madrid 
\item[CuadRom-long] Cuadernos de trabajos de la Escuela española de historia y arqueología en Roma 
\item[CuPaUAM-long] Cuadernos de prehistoria y arqueología. Universidad autónoma de Madrid 
\item[CVA-long] Corpus vasorum antiquorum 
\item[CZero-long] Cota Zero. Revista d'arqueologia i ciencia 
\item[DAA-long] Denkmäler antiker Architektur 
\item[Dacia-long] Dacia. Revue d'archéologie et d'histoire ancienne 
\item[DACL-long] Dictionnaire d'archéologie chrétienne et de liturgie 
\item[Dacoromania-long] Dacoromania. Jahrbuch für östliche Latinität 
\item[DaF-long] Damaszener Forschungen 
\item[Daidalos-long] Daidalos. Studi e ricerche del Dipartimento di scienze del mondo antico 
\item[DAIGeschDok-long] Das Deutsche Archäologische Institut. Geschichte und Dokumente 
\item[DaM-long] Damaszener Mitteilungen 
\item[Daremberg-Saglio-long] Dictionnaire des antiquités grecques et romaines d'après les textes et les monuments. Ouvrage rédigé sous la direction de Ch. Daremberg et E. Saglio %*Abweichung!
\item[DebrecMuzEvk-long] A Debreceni Déri múzeum évkönyve 
\item[Dedalo-long] Dédalo. Revista de arte e arqueologia %*Abweichung!
\item[Delos-long] Exploration archéologique de Délos faite par l'École française d'Athènes %*Abweichung!
\item[DeltChrA-long] Δελτίον της Χριστιανικής Αρχαιολογικής Εταιρείας 
\item[Demircihueyuek-long] Demircihüyük. Die Ergebnisse der Ausgrabungen 1975--1978 %*Abweichung!
\item[DeMuseus-long] De museus. Quaderns de museologia i museografia 
\item[DenkmPflBadWuert-long] Denkmalpflege in Baden-Württemberg %*Abweichung!
\item[DenkschrWien-long] Österreichische Akademie der Wissenschaften, Philosophisch-Historische Klasse. Denkschriften 
\item[Diadora-long] Diadora. Glasilo arheoloskog muzeja u Zadru 
\item[DialA-long] Dialoghi di archeologia 
\item[DialHistAnc-long] Dialogues d'histoire ancienne 
\item[Dike-long] Dike. Rivista di storia del diritto greco ed ellenistico. Università degli studi di Milano. Facoltà di giurisprudenza 
\item[Dioniso-long] Dioniso. Annale della Fondazione INDA, Istituto nazionale del dramma antico 
\item[DiskAB-long] Diskussionen zur archäologischen Bauforschung 
\item[DKuDenkmPfl-long] Deutsche Kunst und Denkmalpflege 
\item[DLZ-long] Deutsche Literaturzeitung für Kritik der internationalen Wissenschaft 
\item[DNP-long] Der Neue Pauly. Enzyklopädie der Antike 
\item[DocAlb-long] Documenta Albana 
\item[DocALouv-long] Documents d'archéologie régionale. Université catholique de Louvain 
\item[DocAMerid-long] Documents d'archéologie méridionale 
\item[DocEmRom-long] Documenti. Istituto per i beni artistici, culturali, naturali della regione Emilia-Romagna 
\item[Dodone-long] Δωδώνη 
\item[DOP-long] Dumbarton Oaks Papers 
\item[DossAlet-long] Les dossiers du Centre régional archéologique d'Alet 
\item[DossAParis-long] Les dossiers d'archéologie 
\item[Dura-Europos-long] The Excavations at Dura-Europos Conducted by Yale University and the French Academy of Inscriptions and Letters 
\item[EAA-long] Enciclopedia dell'arte antica classica e orientale 
\item[EAE-long] Excavaciones arqueológicas en España 
\item[EastWest-long] East and West 
\item[EcAntNimes-long] École antique de Nîmes. Bulletin annuel 
\item[EchosCl-long] Echos du monde classique. Classical Views 
\item[eDAI-F-long] e-Forschungsberichte des Deutschen Archäologischen Instituts 
\item[eDAI-J-long] e-Jahresberichte des Deutschen Archäologischen Instituts 
\item[EgA-long] Egyptian Archaeology. The Bulletin of the Egypt Exploration Society 
\item[Egnatia-long] Εγνατία. Επιστημονική Επετηρίδα της Φιλοσοφικής Σχολής, Αριστοτέλειο Πανεπιστήμιο Θεσσαλονίκης, Τμήμα Ιστορίας και Αρχαιολογίας 
\item[EgVicOr-long] Egitto e Vicino Oriente 
\item[Eikasmos-long] Εικασμός. Quaderni bolognesi di filologia classica 
\item[Eirene-long] Eirene. Studia Graeca et Latina 
\item[Elenchos-long] Elenchos. Rivista di studi sul pensiero antico 
\item[Ellenika-long] Ελληνικά. Φιλολογικόν, Ιστορικόν και Λαογραφικόν Περιοδικόν Σύγγραμμα 
\item[Emerita-long] Emerita. Revista de linguistica y filología clasica 
\item[EmPrerom-long] Emilia preromana 
\item[Empuries-long] Empúries. Revista de prehistòria, arqueologia i etnologia %*Abweichung!
\item[Enalia-long] Ενάλια 
\item[EnaliaAnn-long] Enalia. Annual. English Edition of the Hellenic Institute of Marine Archaeology 
\item[Enchoria-long] Enchoria. Zeitschrift für Demotistik und Koptologie 
\item[Eos-long] Eos. Commentarii Societatis philologae Polonorum 
\item[EpetBoiotMel-long] Επετηρίς της Εταιρείας Βοιωτικών Μελετών 
\item[EpetByzSpud-long] Επετηρίς της Εταιρείας Βυζαντινών Σπουδών 
\item[EpetKyklMel-long] Επετηρίς της Εταιρείας Κυκλαδικών Μελετών 
\item[EphemDac-long] Ephemeris Dacoromana. Annuario della Scuola Romena di Roma 
\item[EphemNapoc-long] Ephemeris Napocensis 
\item[EpigrAnat-long] Epigraphica Anatolica. Zeitschrift für Epigraphik und historische Geographie Anatoliens 
\item[EpistEpetAth-long] Επιστημονική Επετηρίς της Φιλοσοφικής Σχολής του Πανεπιστημίου Αθηνών 
\item[EpistEpetPolytThess-long] Επιστημονική Επετηρίδα της Πολυτεχνικής Σχολής, Αριστοτέλειο Πανεπιστήμιο Θεσσαλονίκης, Τμήμα Αρχιτεκτόνων 
\item[EpistEpetThess-long] Επιστημονική Επετηρίδα της Φιλοσοφικής Σχολής του Πανεπιστημίου Θεσσαλονίκης 
\item[EPRO-long] Études préliminaires aux religions orientales dans l'empire romain 
\item[Eranos-long] Eranos. Acta philologica Suecana 
\item[EranosJb-long] Eranos-Jahrbuch 
\item[Eretria-long] Eretria. Fouilles et recherches 
\item[Eretz-Israel-long] Eretz-Israel. Archaeological, Historical and Geographical Studies 
\item[Ergon-long] Το Έργον της Αρχαιολογικής Εταιρείας 
\item[ESA-long] Eurasia septentrionalis antiqua 
\item[EspacioHist-long] Espacio, tiempo y forma. Revista de la Facultad de geografia e historia. Serie 2, Historia antigua 
\item[EstMadr-long] Estudios de prehistoria y arqueología madrileñas 
\item[EstZaragoza-long] Estudios del Seminario de prehistoria, arqueología e historia antigua de la Facultad de filosofía y letras de Zaragoza 
\item[EtACl-long] Études d'archéologie classique 
\item[EtCl-long] Les études classiques. Revue trimestrielle de recherche et d'enseignement 
\item[EtClAix-long] Études classiques. Faculté des lettres et sciences humaines d'Aix 
\item[EtCret-long] Études crétoises 
\item[Ethnos-long] Ethnos. Revista do Instituto português de arqueología, história e etnografia 
\item[EtP-long] Études de papyrologie 
\item[EtPezenas-long] Études sur Pézenas et l'Hérault %*Abweichung!
\item[EtrSt-long] Etruscan Studies. Journal of the Etruscan Foundation 
\item[Etruscans-long] Etruscans. Bulletin of the Etruscan Foundation 
\item[EtTrav-long] Études et travaux. Studia i prace. Travaux du Centre d'archéologie méditerranéenne de l'Académie des sciences polonaise 
\item[Eulimene-long] Ευλιμένη (Μεσογειακή Αρχαιολογική Εταιρεία) 
\item[Eunomia-long] Eunomia. Ephemeridis Listy filologické supplementum 
\item[Euphrosyne-long] Euphrosyne. Revista de filologia clássica 
\item[EurAnt-long] Eurasia antiqua 
\item[EurRHist-long] European Review of History. Revue européenne d'histoire 
\item[Eutopia-long] Eutopia. Commentarii novi de antiquitatibus totius Europae 
\item[EVP-long] J. D. Beazley, Etruscan Vase Painting (Oxford 1947) 
\item[ExcIsr-long] Excavations and Surveys in Israel 
\item[Expedition-long] Expedition. The Magazine of Archaeology, Anthropology 
\item[ExtremA-long] Extremadura arqueológica 
\item[FA-long] Fasti archaeologici 
\item[FAAK-long] Forschungen zur Archäologie Außereuropäischer Kulturen 
\item[Faenza-long] Faenza. Bollettino del Museo internazionale delle ceramiche in Faenza. Rivista bimestrale di studi storici e di tecnica dell'arte ceramica 
\item[FAVA-long] Forschungen zur Allgemeinen und Vergleichenden Archäologie 
\item[Faventia-long] Faventia. Departement de clássiques, Facultat de letres, Universitat autónoma de Barcelona 
\item[FBerBadWuert-long] Forschungen und Berichte zur Vor- und Frühgeschichte in Baden-Württemberg %*Abweichung!
\item[FdC-long] Fouilles de Conimbriga. Publiées sous la direction de J. Alarcão et R. Etienne 
\item[FdD-long] Fouilles de Delphes 
\item[FdX-long] Fouilles de Xanthos 
\item[FeddersenWierde-long] Feddersen Wierde. Die Ergebnisse der Ausgrabung der vorgeschichtlichen Wurt Feddersen Wierde bei Bremerhaven in den Jahren 1955 bis 1963 %*Abweichung!
\item[FelRav-long] Felix Ravenna 
\item[FGrHist-long] F. Jacoby, Die Fragmente der griechischen Historiker 
\item[FHG-long] Fragmenta historicorum Graecorum 
\item[FiA-long] Forschungen in Augst 
\item[FichEpigr-long] Ficheiro epigráfico. Suplemento de »Conimbriga« 
\item[FiE-long] Forschungen in Ephesos 
\item[FIFAO-long] Fouilles de l'Institut français d'archéologie orientale du Caire 
\item[Figlina-long] Figlina. Documents du Laboratoire de céramologie de Lyon 
\item[Florentia-long] Florentia. Studi di archeologia 
\item[FlorIl-long] Florentia Iliberritana. Revista de estudios de antigüedad clásica 
\item[FMRD-long] Die Fundmünzen der römischen Zeit in Deutschland 
\item[FMROe-long] Fundmünzen der römischen Zeit in Österreich %*Abweichung!
\item[FoggArtMusAcqu-long] Fogg Art Museum. Acquisitions 
\item[FolA-long] Folia archaeologica 
\item[FolOr-long] Folia orientalia 
\item[Fonaments-long] Fonaments. Prehistòria i mon antic als Paisos Catalans 
\item[Fondamenti-long] Fondamenti. Rivista quadrimestrale di cultura 
\item[FontAPos-long] Fontes archaeologici Posnanienses 
\item[Fontes-long] Fontes. Rivista di filologia, iconografia e storia della tradizione classica 
\item[Forlimpopoli-long] Forlimpopoli. Documenti e studi 
\item[Fornvaennen-long] Fornvännen. Tidskrift för svensk antikvarisk forskning %*Abweichung!
\item[Forum-long] Forum. Revue du Groupe d'archéologie antique 
\item[FR-long] A. Furtwängler – K. Reichhold, Griechische Vasenmalerei (München 1900--1925) 
\item[FruehMitAltSt-long] Frühmittelalterliche Studien. Jahrbuch des Instituts für Frühmittelalterforschung der Universität Münster %*Abweichung!
\item[FuAusgrTrier-long] Funde und Ausgrabungen im Bezirk Trier 
\item[FuB-long] Forschungen und Berichte. Staatliche Museen zu Berlin 
\item[FuBerBadWuert-long] Fundberichte aus Baden-Württemberg %*Abweichung!
\item[FuBerHessen-long] Fundberichte aus Hessen 
\item[FuBerOe-long] Fundberichte aus Österreich %*Abweichung!
\item[FuBerSchwab-long] Fundberichte aus Schwaben 
\item[FuF-long] Forschungen und Fortschritte 
\item[FuWien-long] Fundort Wien. Berichte zur Archäologie 
\item[GacNum-long] Gaceta numismática 
\item[Gades-long] Gades. Revista del Colegio universitario de filosofía y letras 
\item[Gallaecia-long] Gallaecia. Publicación del Departamento de prehistoria y arqueología 
\item[Gallia-long] Gallia. Fouilles et monuments archéologiques en France metropolitaine 
\item[GalliaInf-long] Gallia informations. Préhistoire et histoire 
\item[GalliaInfAReg-long] Gallia informations. L'archéologie des régions 
\item[GalliaPrehist-long] Gallia préhistoire. Archéologie de la France préhistorique 
\item[GaR-long] Greece and Rome 
\item[GazBA-long] Gazette des beaux-arts 
\item[Genava-long] Genava. Revue d'histoire de l'art et d'archéologie 
\item[GeoAnt-long] Geographia antiqua. Rivista di geografia storica del mondo antico e di storia della geografia 
\item[Germania-long] Germania. Anzeiger der Römisch-Germanischen Kommission des Deutschen Archäologischen Instituts 
\item[Gesta-long] Gesta. International Center of Medieval Art 
\item[GettyMusJ-long] The J. Paul Getty Museum Journal 
\item[GFA-long] Göttinger Forum für Altertumswissenschaft 
\item[GGA-long] Göttingische Gelehrte Anzeigen 
\item[GiornFilFerr-long] Giornale filologico ferrarese 
\item[GiornItFil-long] Giornale italiano di filologia 
\item[GiornStorLun-long] Giornale storico della Lunigiana e del territorio lucense 
\item[GiRoccPalermo-long] Giglio di roccia 
\item[Gladius-long] Gladius. Estudios sobre armas antiguas, armamento, arte militar y vida cultural en Oriente y Occidente 
\item[GlasAJ-long] Glasgow Archaeological Journal 
\item[GlasBeograd-long] GlasnikSrpskoarheolokodrutvo 
\item[GlasSarajevo-long] Glasnik Zemaljskog muzeja Bosne i Hercegovie u Sarajevu. Arheologija 
\item[Glotta-long] Glotta. Zeitschrift für griechische und lateinische Sprache 
\item[Gnomon-long] Gnomon. Kritische Zeitschrift für die gesamte klassische Altertumswissenschaft 
\item[GodDepA-long] Godišnik na Departament archeologija 
\item[GodMuzPlov-long] Godišnik na Archeologičeski muzej Plovdiv. Annuaire du Musée archéologique Plovdiv 
\item[GodMuzSof-long] Godišnik na Nacionalnija archeologičeski muzej. Annuaire du Musée national archéologique (Sofia) 
\item[GodZborSkopje-long] Godišen zbornik na Filozofskiot fakultet na Universitetot vo Skopje 
\item[GorLet-long] Goriški letnik. Zbornik Goriškega muzeja 
\item[GoettMisz-long] Göttinger Miszellen. Beiträge zur ägyptologischen Diskussion %*Abweichung!
\item[GraRaspr-long] Građa i rasprave. Arheološki muzej Istre, Pula 
\item[GrazBeitr-long] Grazer Beiträge. Zeitschrift für die Klassische Altertumswissenschaft 
\item[GrLatOr-long] Graecolatina et orientalia. Zborník Filozofickej fakulty Univerzity Komenského 
\item[GrLatPrag-long] Graecolatina Pragensia. Acta Universitatis Carolinae. Philologica 
\item[GrRomByzSt-long] Greek, Roman and Byzantine Studies 
\item[Gymnasium-long] Gymnasium. Zeitschrift für Kultur der Antike und humanistische Bildung 
\item[Habis-long] Habis. Universidad de Sevilla. Arqueología, filología clásica 
\item[HallWPr-long] Hallisches Winckelmannsprogramm 
\item[Hama-long] Hama. Fouilles et recherches de la Fondation Carlsberg 
\item[HambBeitrA-long] Hamburger Beiträge zur Archäologie 
\item[HambBeitrNum-long] Hamburger Beiträge zur Numismatik 
\item[Handlingar-long] Kungliga vitterhets historie och antikvitets akademiens handlingar. Antikvariska serien 
\item[HarvStClPhil-long] Harvard Studies in Classical Philology 
\item[HarvTheolR-long] The Harvard Theological Review 
\item[HASB-long] Hefte des Archäologischen Seminars der Universität Bern 
\item[HAW-long] Handbuch der Altertumswissenschaften 
\item[HdArch-long] Handbuch der Archäologie 
\item[Head-long] B. V. Head, Historia Numorum. A Manual of Greek Numismatics (Oxford 1887; 1911) 
\item[Helbig-long] W. Helbig, Führer durch die öffentlichen Sammlungen klassischer Altertümer in Rom 
\item[Helike-long] Helike. Universidad nacional de educación a distancia, Centro regional de Elche 
\item[Helikon-long] Helikon. Rivista di tradizione e cultura classica 
\item[Helinium-long] Helinium. Revue consacrée à l'archéologie des Pays-Bas, de la Belgique et du Grand-Duché de Luxembourg 
\item[Helios-long] Helios. A Journal Devoted to Critical and Methodological Studies of Classical Culture, Literature and Society 
\item[HellenikaJb-long] Hellenika. Jahrbuch für die Freunde Griechenlands 
\item[HelvA-long] Helvetia archaeologica 
\item[Hephaistos-long] Hephaistos. Kritische Zeitschrift zur Theorie und Praxis der Archäologie und angrenzender Wissenschaften 
\item[Hermes-long] Hermes. Zeitschrift für klassische Philologie 
\item[Herrscherbild-long] Das römische Herrscherbild 
\item[Hesperia-long] Hesperia. Journal of the American School of Classical Studies at Athens 
\item[Hispania-long] Hispania. Revista española de historia 
\item[HispAnt-long] Hispania antiqua. Revista de historia antigua 
\item[HispAntEpigr-long] Hispania antiqua epigraphica 
\item[HispEpigr-long] Hispania epigraphica 
\item[HistAnthr-long] Historische Anthropologie. Kultur, Gesellschaft, Alltag 
\item[HistArt-long] Histoire de l'art. Bulletin d'information de l'Institut National d'Histoire de l'Art 
\item[Historia-long] Historia. Zeitschrift für Alte Geschichte 
\item[Historica-long] Historica. Academia RSR. Centrul de istorie, filologie şi etnografie din Craiova 
\item[Histria-long] Histria. Les résultats des fouilles 
\item[HistriaA-long] Histria archaeologica 
\item[HistriaAnt-long] Histria antiqua. Casopis Meunarodnog Istraivakog Centra za Arheologiju. Journal of the International Research Centre for Archeology 
\item[HistSprF-long] Historische Sprachforschung 
\item[HKL-long] R. Borger, Handbuch der Keilschriftliteratur (Berlin 1967--1975) 
\item[Horos-long] Ηόρος. Ἔνα Ἀρχαιογνωστικò Περιοδικό 
\item[HSS-long] Harvard Semitic Series 
\item[HuelvaA-long] Huelva arqueológica 
\item[HumBild-long] Humanistische Bildung 
\item[Hyp-long] Hyperboreus. Studia classica 
\item[HZ-long] Historische Zeitschrift 
\item[IA-long] Iberia archaeologica 
\item[Iberia-long] Iberia. Revista della antigüedad 
\item[IEJ-long] Israel Exploration Journal 
\item[IG-long] Inscriptiones Graecae 
\item[IGCH-long] M. Thompson – C. M. Kraay – O. Mørkholm, An Inventory of Greek Coin Hoards (New York 1973) 
\item[IGR-long] Inscriptiones Graecae ad res Romanas pertinentes 
\item[IK-long] Inschriften griechischer Städte aus Kleinasien 
\item[Ilerda-long] Ilerda. Instituto de estudios ilerdenses 
\item[Iliria-long] Iliria. Revistë arkeologjike 
\item[IllinClSt-long] Illinois Classical Studies 
\item[ILN-long] The Illustrated London News 
\item[ILS-long] H. Dessau, Inscriptiones Latinae selectae (Berlin 1892--1916) 
\item[IndexQuad-long] Index. Quaderni camerti di studi romanistici 
\item[IndogermF-long] Indogermanische Forschungen 
\item[IndUnArtB-long] Indiana University Art Museum Bulletin 
\item[InsFulc-long] Insula Fulcheria 
\item[InstNautAQ-long] The Institute of Nautical Archaeology Quarterly 
\item[IntJClTrad-long] International Journal of the Classical Tradition 
\item[IntJNautA-long] International Journal of Nautical Archaeology 
\item[IntZSchauBibelWiss-long] Internationale Zeitschriftenschau für Bibelwissenschaft und Grenzgebiete 
\item[InvLuc-long] Invigilata lucernis 
\item[Ipek-long] Jahrbuch für prähistorische und ethnographische Kunst 
\item[Iran-long] Iran. Journal of the British Institute of Persian Studies 
\item[IrAnt-long] Iranica antiqua 
\item[IsrMusJ-long] The Israel Museum Journal 
\item[IsrMusN-long] The Israel Museum News 
\item[IsrMusStA-long] Israel Museum Studies in Archaeology. An Annual Publication by the Samuel Bronfman Biblical and Archaeological Museum of the Israel Museum, Jerusalem 
\item[IsrNumJ-long] Israel Numismatic Journal 
\item[IstanbAMuezYil-long] Istanbul Arkeoloji Müzeleri yıllığı %*Abweichung!
\item[IstForsch-long] Istanbuler Forschungen 
\item[Isthmia-long] Isthmia. Excavations by the University of Chicago under the Auspices of the American School of Classical Studies at Athens 
\item[IstMitt-long] Istanbuler Mitteilungen 
\item[Italica-long] Italica. Cuadernos de trabajos de la Escuela española de historia y arqueología en Roma 
\item[ItNostr-long] Italia nostra 
\item[IzvBurgas-long] Izvestija na Narodnija muzej Burgas. Bulletin du Musée national de Bourgas 
\item[IzvMuzJuzBalg-long] Izvestija na muzeite ot Južna Bălgarija. Bulletin des musées de la Bulgarie du Sud %*Abweichung
\item[IzvVarna-long] Izvestija na Narodnija muzej Varna 
\item[Jabega-long] Jábega. Revista de la Disputación provincial de Málaga %*Abweichung!
\item[JadrZbor-long] Jadranski zbornik. Prilozi za povijest Istre, Rijeke i Hrvatskog primorja 
\item[JAOS-long] Journal of the American Oriental Society 
\item[JARCE-long] Journal of the American Research Center in Egypt 
\item[JASc-long] Journal of Archaeological Science 
\item[JbAC-long] Jahrbuch für Antike und Christentum 
\item[JbAkMainz-long] Jahrbuch. Akademie der Wissenschaften und der Literatur, Mainz 
\item[JbBadWuert-long] Jahrbuch der Staatlichen Kunstsammlungen in Baden-Württemberg %*Abweichung!
\item[JbBerlMus-long] Jahrbuch der Berliner Museen 
\item[JbBernHistMus-long] Jahrbuch des Bernischen Historischen Museums in Bern 
\item[JberAugst-long] Jahresberichte aus Augst und Kaiseraugst 
\item[JberBasel-long] Jahresbericht der Archäologischen Bodenforschung des Kantons Basel-Stadt 
\item[JberBayDenkmPfl-long] Jahresbericht der Bayerischen Bodendenkmalpflege 
\item[JberProVindon-long] Jahresbericht. Gesellschaft Pro Vindonissa 
\item[JberVgFrankf-long] Jahresbericht des Instituts für Vorgeschichte der Universität Frankfurt a. M. 
\item[JberZuerich-long] Jahresbericht. Schweizerisches Landesmuseum Zürich %*Abweichung!
\item[JbGoett-long] Jahrbuch der Akademie der Wissenschaften in Göttingen %*Abweichung!
\item[JbHambKuSamml-long] Jahrbuch der Hamburger Kunstsammlungen 
\item[JbKHMWien-long] Jahrbuch des Kunsthistorischen Museums Wien 
\item[JbKHSWien-long] Jahrbuch der Kunsthistorischen Sammlungen in Wien 
\item[JbKleinasF-long] Jahrbuch für kleinasiatische Forschung 
\item[JbMuench-long] Bayerische Akademie der Wissenschaften. Jahrbuch %*Abweichung!
\item[JbMusKGHamb-long] Jahrbuch des Museums für Kunst und Gewerbe, Hamburg 
\item[JbMusLinz-long] Jahrbuch des Oberösterreichischen Musealvereins 
\item[JbOeByz-long] Jahrbuch der Österreichischen Byzantinistik %*Abweichung!
\item[JbPreussKul-long] Jahrbuch Preussischer Kulturbesitz 
\item[JbRGZM-long] Jahrbuch des Römisch-Germanischen Zentralmuseums Mainz 
\item[JbSchwUrgesch-long] Jahrbuch der Schweizerischen Gesellschaft für Ur- und Frühgeschichte 
\item[JCS-long] Journal of Cuneiform Studies 
\item[JdI-long] Jahrbuch des Deutschen Archäologischen Instituts 
\item[JEA-long] The Journal of Egyptian Archaeology 
\item[JEChrSt-long] Journal of Early Christian Studies. Journal of the North American Patristics Society 
\item[JEOL-long] Jaarbericht van het Vooraziatisch-Egyptisch Genootschap Ex Oriente Lux 
\item[JewelSt-long] Jewellery Studies 
\item[JFieldA-long] Journal of Field Archaeology 
\item[JGS-long] Journal of Glass Studies 
\item[JHS-long] The Journal of Hellenic Studies 
\item[JIbA-long] Journal of Iberian Archaeology 
\item[JJurP-long] The Journal of Juristic Papyrology 
\item[JKuGesch-long] Journal für Kunstgeschichte 
\item[JMedA-long] Journal of Mediterranean Archaeology 
\item[JMedAnthrA-long] Journal of Mediterranean Anthropology and Archaeology 
\item[JMithrSt-long] Journal of Mithraic Studies 
\item[JNES-long] Journal of Near Eastern Studies 
\item[JNG-long] Jahrbuch für Numismatik und Geldgeschichte 
\item[JPrehistRel-long] Journal of Prehistoric Religion 
\item[JRA-long] Journal of Roman Archaeology 
\item[JRomMilSt-long] Journal of Roman Military Equipment Studies 
\item[JRomPotSt-long] Journal of Roman Pottery Studies 
\item[JRS-long] The Journal of Roman Studies 
\item[JSav-long] Journal des savants 
\item[JSchrVgHalle-long] Jahresschrift für mitteldeutsche Vorgeschichte 
\item[JSS-long] Journal of Semitic Studies 
\item[JTheorA-long] Journal of Theoretical Archaeology 
\item[Jura-long] Iura. Rivista internazionale di diritto romano e antico 
\item[JWaltersArtGal-long] The Journal of the Walters Art Gallery 
\item[JWCI-long] Journal of the Warburg and Courtauld Institutes 
\item[Kadmos-long] Kadmos. Zeitschrift für vor- und frühgriechische Epigraphik 
\item[Kairos-long] Kairos. Zeitschrift für Judaistik und Religionswissenschaft 
\item[Kalapodi-long] Kalapodi. Ergebnisse der Ausgrabungen im Heiligtum der Artemis und des Apollon von Hyampolis in der antiken Phokis 
\item[Kalathos-long] Kalathos. Revista del Seminario de arqueología y etnología Turolense, Universidad de Teruel 
\item[Kalos-long] Kalós. Arte in Sicilia %*Abweichung!
\item[Karthago-long] Karthago. Revue d'archéologie mediterranéenne 
\item[Kemi-long] Kêmi. Revue de philologie et d'archéologie égytiennes et coptes %*Abweichung!
\item[Kenchreai-long] Kenchreai. Eastern Port of Corinth. Results of Investigations by the University of Chicago and Indiana University for the American School of Classical Studies at Athens 
\item[KentAR-long] Kent Archaeological Review 
\item[Keos-long] Keos. Results of Excavations Conducted by the University of Cincinnati under the Auspices of the American School of Classical Studies at Athens 
\item[Kerameikos-long] Kerameikos. Ergebnisse der Ausgrabungen 
\item[Kernos-long] Kernos. Revue internationale et pluridisciplinaire de religion grecque antique 
\item[Klearchos-long] Klearchos. Bollettino dell'Associazione Amici del Museo nazionale di Reggio Calabria 
\item[Kleos-long] Kleos. Estemporaneo di studi e testi sulla fortuna dell'antico 
\item[Klio-long] Klio. Beiträge zur alten Geschichte 
\item[Kodai-long] Kodai. Journal of Ancient History 
\item[KoelnJb-long] Kölner Jahrbuch %*Abweichung!
\item[KoelnMusB-long] Kölner Museums-Bulletin. Berichte und Forschungen aus den Museen der Stadt Köln %*Abweichung!
\item[Kokalos-long] Kώκαλος. Studi pubblicati dall’Istituto di storia antica dell’Università di Palermo %*Abweichung!
\item[KollAVA-long] Kolloquien zur Allgemeinen und Vergleichenden Archäologie 
\item[Kratylos-long] Kratylos. Kritisches Berichts- und Rezensionsorgan für indogermanische und allgemeine Sprachwissenschaft 
\item[KretChron-long] Κρητικά Χρονικά 
\item[KSIA-long] Kratkie soobščenija o dokladach i polevych issledovanijach Instituta archeologii 
\item[KSIAKiev-long] Kratkie soobščenija Instituta archeologii, Kiev 
\item[KST-long] Kazı Sonuçları Toplantısı 
\item[Ktema-long] Ktema. Civilisations de l'Orient, de la Grèce et de Rome antiques 
\item[KuGeschAnz-long] Kunstgeschichtliche Anzeigen 
\item[Kuml-long] Kuml. Årbog for Jysk Arkaeologisk Selskab 
\item[Kunstchronik-long] Kunstchronik. Monatsschrift für Kunstwissenschaft, Museumswesen und Denkmalpflege, Mitteilungsblatt des Verbandes Deutscher Kunsthistoriker 
\item[KuOr-long] Kunst des Orients 
\item[Kush-long] Kush. Journal of the National Corporation for Antiquities and Museums (NCAM) 
\item[KuWeltBerlMus-long] Kunst der Welt in den Berliner Museen 
\item[KypA-long] Κυπριακή Αρχαιολογία. Archaeologia Cypria 
\item[KypSpud-long] Κυπριακαì Σπουδαί 
\item[Labeo-long] Labeo. Rassegna di ritritto romano 
\item[LAe-long] Lexikon der Ägyptologie %*Abweichung!
\item[Laietania-long] Laietania. Estudios d'arqueologia del Maresme 
\item[Lampas-long] Lampas. Tijdschrift voor nederlandse classici 
\item[Lancia-long] Lancia. Revista de prehistoria, arqueología e historia antigua del noreste peninsular 
\item[LandKunVierJBl-long] Landeskundliche Vierteljahrsblätter. Trier 
\item[LangOrAnc-long] Langues orientales anciennes. Philologie et linguistique 
\item[Latinitas-long] Latinitas. Commentarii linguae Latinae excolendae provehendae 
\item[Latomus-long] Latomus. Revue d'études latines 
\item[Laverna-long] Laverna. Beiträge zur Wirtschafts- und Sozialgeschichte der Alten Welt 
\item[LCS-long] A. D. Trendall, The Red-figured Vases of Lucania, Campania and Sicily (Oxford 1967--­1983) 
\item[Levant-long] Levant. Journal of the British School of Archaeology in Jerusalem and the British Institute at Amman for Archaeology and History 
\item[Lexis-long] Lexis. Poetica, retorica e comunicazione nella tradizione classica 
\item[LF-long] Listy filologické 
\item[LibSt-long] Libyan Studies 
\item[LibyaAnt-long] Libya antiqua 
\item[LibycaBServAnt-long] Libyca. Bulletin du Service des antiquités. Archéologie, épigraphie 
\item[LibycaTrav-long] Libyca. Travaux du Laboratoire d'anthropologie et d'archéologie préhistorique du Musée du Bardo 
\item[Liddell-­Scott-Jones-long] G. Liddell – R. Scott – H. S. Jones, A Greek-English Lexikon \textsuperscript{9}(1996); Suppl. (1996) %*Abweichung!
\item[LIMC-long] Lexikon iconographicum mythologiae classicae 
\item[Limesforschungen-long] Limesforschungen. Studien zur Organisation der römischen Reichsgrenze an Rhein und Donau 
\item[Lindos-long] Lindos. Fouilles et recherches 
\item[LingIt-long] Linguistica, epigrafia, filologia italica 
\item[LTUR-long] Lexikon topographicum urbis Romae 
\item[Lucentum-long] Lucentum. Anales de la Universidad de Alicante. Prehistoria, arqueología e historia antigua 
\item[LundAR-long] Lund Archaeological Review 
\item[Lustrum-long] Lustrum. Internationale Forschungsberichte aus dem Bereich des klassischen Altertums 
\item[Lykia-long] Lykia. Anadolu-akdeniz kültürleri 
\item[MacActaA-long] Macedoniae acta archaeologica 
\item[Maecenas-long] Maecenas. Studi sul mondo classico 
\item[MAGesGraz-long] Mitteilungen der Archäologischen Gesellschaft Graz 
\item[MAGesStei-long] Mitteilungen der Archäologischen Gesellschaft Steiermark 
\item[Maia-long] Maia. Rivista di letterature classiche 
\item[Mainake-long] Mainake. Estudios de arqueología Malagueña 
\item[MAInstUngAk-long] Mitteilungen des Archäologischen Instituts der Ungarischen Akademie der Wissenschaften 
\item[MainzZ-long] Mainzer Zeitschrift 
\item[MakedNasl-long] Makedonsko nasledstvo. Spisanie za arheologija, istorija, istorija na umetnosta i etnologija 
\item[Makedonika-long] Μακεδονικά. Σύγγραμμα Περιοδικόν της Εταιρείας Μακεδονικών Σπουδών 
\item[MAMA-long] Monumenta Asiae Minoris antiqua. Publications of the American Society for Archaeological Research in Asia Minor 
\item[MAnthrWien-long] Mitteilungen der Anthropologischen Gesellschaft in Wien 
\item[MAR-long] Monumenta artis Romanae 
\item[MarbWPr-long] Marburger Winckelmann-Programm 
\item[Marche-long] Le Marche. Archeologia, storia, territorio 
\item[Mari-long] Mari. Annales de recherches interdisciplinaires 
\item[Marisia-long] Marisia. Studii şi materiale. Arheologie, istorie, etnografie 
\item[MarNero-long] Il Mar Nero. Annali di archeologia e storia 
\item[Marsyas-long] Marsyas. Studies in the History of Art 
\item[MascaJ-long] Masca Journal. Museum Applied Science Center for Archaeology, University of Pennsylvania 
\item[MascaP-long] Masca Research Papers in Science and Archaeology 
\item[Mastia-long] Mastia. Revista del Museo arqueológico municipal de Cartagena 
\item[MatABSSR-long] Materialy po archeologii BSSR 
\item[MatASevPri-long] Materialy po archeologii severnogo Pričernomor’ja 
\item[MatCercA-long] Materiale şi cercetări arheologice 
\item[MatIsslA-long] Materialy i issledovanija po archeologii SSSR 
\item[MatStar-long] Materiały starożytne 
\item[MatStarWczes-long] Materiały starożytne i wczesnośredniowieczne 
\item[MatTestiCl-long] Materiali e discussioni per l'analisi dei testi classici 
\item[MatWczes-long] Materiały wczesnośredniowieczne 
\item[MAVA-long] Materialien zur Allgemeinen und Vergleichenden Archäologie 
\item[MB-long] Madrider Beiträge 
\item[MBAH-long] Marburger Beiträge zur antiken Handels-, Wirtschafts- und Sozialgeschichte, vor Jahrgang 2009 Münstersche Beiträge zur antiken Handelsgeschichte 
\item[MBlVFruehGesch-long] Mitteilungsblatt für Vor- und Frühgeschichte %*Abweichung!
\item[MDAIK-long] Mitteilungen des Deutschen Archäologischen Instituts, Abteilung Kairo 
\item[MDAVerb-long] Mitteilungen des Deutschen Archäologen-Verbandes e.V. 
\item[MdI-long] Mitteilungen des Deutschen Archäologischen Instituts 
\item[MDOG-long] Mitteilungen der Deutschen Orient-Gesellschaft zu Berlin 
\item[Meander-long] Meander. Miesięcznik poświęcony kulturze świata starożytnego 
\item[MedA-long] Mediterranean Archaeology 
\item[MedAnt-long] Mediterraneo antico. Economie, società, culture 
\item[MeddelGlypt-long] Meddelelser fra Ny Carlsberg Glyptotek 
\item[MeddelLund-long] Meddelanden från Lunds universtitets historiska museum 
\item[MeddelThor-long] Meddelelser fra Thorvaldsens Museum 
\item[MededRom-long] Mededelingen van het Nederlands instituut te Rome 
\item[MedelhavsMusB-long] Medelhavsmuseet. Bulletin 
\item[MedHistR-long] Mediterranean Historical Review 
\item[MedievA-long] Medieval Archaeology. Journal of the Society for Medieval Archaeology 
\item[MediSec-long] Medicina nei secoli. Arte e scienza 
\item[MEFRA-long] Mélanges de l'École française de Rome. Antiquité 
\item[MelBeyrouth-long] Mélanges de l'Université Saint-Joseph 
\item[MelCasaVelazquez-long] Mélanges de la Casa de Velázquez. Antiquité et moyen âge 
\item[MemAcInscr-long] Mémoires de l'Académie des inscriptions et belles-lettres 
\item[MemAmAc-long] Memoirs of the American Academy in Rome 
\item[MemAnt-long] Memoria antiquitatis. Acta Musei Petrodavensis. Revista Muzeului arheologic Piatra Neamţ 
\item[MemAntFr-long] Mémoires de la Société nationale des antiquaires de France 
\item[MemBarcelA-long] Memoria. Universidad de Barcelona, Instituto de arqueología y prehistoria 
\item[MemBologna-long] Atti de la Accademia delle scienze dell'Istituto di Bologna. Memorie 
\item[MemHistAnt-long] Memorias de historia antigua (Universidad de Oviedo) 
\item[MemInstNatFr-long] Mémoires de l'Institut national de France 
\item[MemLinc-long] Atti dell'Accademia nazionale dei Lincei, Classe di scienze morali, storiche e filologiche. Memorie 
\item[MemNap-long] Memorie dell'Accademia di archeologia, lettere e belle arti di Napoli 
\item[MemPontAc-long] Atti della Pontificia accademia romana di archeologia. Memorie 
\item[MemStor-long] Memoria storica. Rivista del Centro studi storici terni 
\item[MemStorFriuli-long] Memorie storiche forogiuliesi 
\item[Merida-long] Mérida. Ciudad y patrimonio %*Abweichung!
\item[MeridaMem-long] Mérida. Excavaciones arqueológicas. Memoria %*Abweichung!
\item[Meroitica-long] Meroitica. Schriften zur altsudanesischen Geschichte und Archäologie 
\item[Mesopotamia-long] Mesopotamia. Rivista di archeologia 
\item[Messana-long] Messana. Rassegna di studi filologici, linguistici e storici 
\item[Metis-long] Métis. Revue d'anthropologie du monde grec ancien %*Abweichung!
\item[MetrMusJ-long] Metropolitan Museum Journal 
\item[MetrMusSt-long] Metropolitan Museum Studies 
\item[MF-long] Madrider Forschungen 
\item[MFruehChrOe-long] Mitteilungen zur frühchristlichen Archäologie in Österreich %*Abweichung!
\item[Milet-long] Milet. Ergebnisse der Ausgrabungen und Untersuchungen seit dem Jahr 1899 
\item[MilForsch-long] Milesische Forschungen 
\item[MinEpigrP-long] Minima epigraphica et papyrologica. Taccuini della cattedra e del laboratorio di epigrafia e papirologia giuridica dell'Università degli studi di Catanzaro »Magna Graecia« 
\item[Minerva-long] Minerva. Revista de filología clásica 
\item[Minos-long] Minos. Revista de filología egea 
\item[MInstWasser-long] Mitteilungen. Leichtweiss-Institut für Wasserbau der Technischen Universität Braunschweig 
\item[MIO-long] Mitteilungen des Instituts für Orientforschung 
\item[MiscCrAnt-long] Miscellanea di studi di letteratura christiana antica 
\item[MiscStStor-long] Miscellanea di studi storici 
\item[MitChrA-long] Mitteilungen zur christlichen Archäologie 
\item[MKT-long] Menschen – Kulturen – Traditionen. Studien aus den Forschungsclustern des Deutschen Archäologischen Instituts 
\item[MKuHistFlorenz-long] Mitteilungen des Kunsthistorischen Institutes in Florenz 
\item[MKul-long] Mitteilungen zur Kulturkunde 
\item[MM-long] Madrider Mitteilungen 
\item[Mnemosyne-long] Mnemosyne. A Journal of Classical Studies 
\item[MOeNumGes-long] Mitteilungen der Österreichischen Numismatischen Gesellschaft %*Abweichung!
\item[MonAnt-long] Monumenti antichi 
\item[MonInst-long] Monumenti inediti pubblicati dall'Istituto Archeologico 
\item[MonPiot-long] Monuments et mémoires. Fondation E. Piot 
\item[MonPitt-long] Monumenti della pittura antica scoperti in Italia 
\item[Mozia-long] Mozia. Rapporto preliminare della missione congiunta con la Soprintendenza alle antichità della Sicilia occidentale 
\item[MPraehistKomWien-long] Mitteilungen der Prähistorischen Kommission der Österreichischen Akademie der Wissenschaften %*Abweichung!
\item[MSAtene-long] Monografie della Scuola archeologica di Atene e delle missioni italiane in Oriente 
\item[MSchliemann-long] Mitteilungen aus dem Heinrich-Schliemann-Museum Ankershagen 
\item[MSchwUrFruehGesch-long] Mitteilungsblatt der Schweizerischen Gesellschaft für Ur- und Frühgeschichte %*Abweichung!
\item[MSpaetAByz-long] Mitteilungen zur spätantiken Archäologie und byzantinischen Kunstgeschichte %*Abweichung!
\item[MueJb-long] Münchner Jahrbuch der bildenden Kunst %*Abweichung!
\item[MuenchBeitrVFG-long] Münchner Beiträge zur Vor- und Frühgeschichte %*Abweichung!
\item[MuenchStSprWiss-long] Münchener Studien zur Sprachwissenschaft %*Abweichung!
\item[MuM-long] Münzen und Medaillen 
\item[MusAfr-long] Museum Africum. West African Journal of Classical and Related Studies 
\item[MusBenaki-long] Μουσείο Μπενάκη 
\item[MusCrit-long] Museum criticum 
\item[Muse-long] Muse. Annual of the Museum of Art and Archaeology, University of Missouri, Columbia 
\item[Museon-long] Le Muséon. Revue d'études orientales %*Abweichung!
\item[MuseumUnesco-long] Museum. A Quarterly Review Published by UNESCO 
\item[MusFerr-long] Musei Ferraresi. Bollettino annuale 
\item[MusGalIt-long] Musei e gallerie d'Italia 
\item[MusHaaretz-long] Museum Haaretz, Tel Aviv. Yearbook 
\item[MusHelv-long] Museum Helveticum 
\item[MusKoeln-long] Museen in Köln. Bulletin %*Abweichung!
\item[MusNotAmNumSoc-long] Museum Notes. The American Numismatic Society 
\item[MusPontevedra-long] El Museo de Pontevedra 
\item[MusRiv-long] Museo in rivista. Notiziario dei Musei civici di Pavia 
\item[MusTusc-long] Museum Tusculanum. København 
\item[MuzEvkSzeged-long] A Móra Ferenc múzeum évkönyve 
\item[MuzNat-long] Muzeul naţional. Bucureşti
\item[MuzPamKul-long] Muzei i pametnici na kulturata 
\item[NachrArbUWA-long] Nachrichtenblatt Arbeitskreis Unterwasserarchäologie 
\item[NapNobil-long] Napoli nobilissima 
\item[NassAnn-long] Nassauische Annalen 
\item[NAWG-long] Nachrichten der Akademie der Wissenschaften in Göttingen. Philologisch-Historische Klasse 
\item[NBWorcArtMus-long] News Bulletin and Calendar. Worcester Art Museum 
\item[NEphemSemEpigr-long] Neue Ephemeris für semitische Epigraphik 
\item[NewsletterAthen-long] Newsletter of the Netherlands Institute at Athens 
\item[NewsletterPotTech-long] Newsletter. Department of Pottery Technology, University of Leiden 
\item[NGWG-long] Nachrichten von der Gesellschaft der Wissenschaften zu Göttingen. Philologisch-Historische Klasse 
\item[NigCl-long] Nigeria and the Classics 
\item[Nikephoros-long] Nikephoros. Zeitschrift für Sport und Kultur im Altertum 
\item[Nin-long] Nin. Journal of Gender Studies in Antiquity 
\item[NNM-long] American Numismatic Society. Numismatic Notes and Monographs 
\item[NomChron-long] Νομισματικά Χρονικά. Περιοδική Έκδωσις της Ελληνικής Νομισματικής Εταιρείας 
\item[Norba-long] Norba. Revista de arte, geografía e historia 
\item[NordNumArs-long] Nordisk numismatisk årsskrift. Utgiven av Kungliga vitterhets historie och antikvitets akademien i samarbete med Nordisk numismatisk union 
\item[NotABerg-long] Notizie archeologiche bergomensi. Periodico di archeologia del Civico museo archeologico di Bergamo 
\item[NotAHisp-long] Noticiario arqueológico hispánico. Arqueología 
\item[NotAHispPrehistoria-long] Noticiario arqueológico hispánico. Prehistoria 
\item[NotAllumiere-long] Notiziario. Museo civico, Associazione archeologica, Allumiere 
\item[NotALomb-long] Notiziario. Soprintendenza archeologica della Lombardia 
\item[NotMilano-long] Notizie dal chiostro del monastero maggiore. Rassegna di studi del Civico museo archeologico e del Civico gabinetto numismatico di Milano 
\item[NouvClio-long] La nouvelle Clio 
\item[Novaensia-long] Novaensia. Badania Ekspedycji archeologicznej Uniwersytetu warszawskiego w Novae 
\item[NSc-long] Notizie degli scavi di antichità 
\item[NStFan-long] Nuovi studi fanesi 
\item[NubChr-long] Nubia christiana 
\item[NubLet-long] Nubian Letters 
\item[NueBlA-long] Nürnberger Blätter zur Archäologie. Publikationsreihe des Bildungszentrums der Stadt Nürnberg, Fachbereich Archäologie %*Abweichung!
\item[NumAntCl-long] Numismatica e antichità classiche. Quaderni ticinesi 
\item[Numantia-long] Numantia. Investigaciones arqueológicas en Castilla y León 
\item[NumChron-long] The Numismatic Chronicle. The Journal of the Royal Society 
\item[Numen-long] Numen. International Review for the History of Religions 
\item[NumEpigr-long] Numizmatika i epigrafika 
\item[Numisma-long] Numisma. Revista de la Sociedad iberoamericana de estudios numismáticos 
\item[NumismaticaRom-long] Numismatica. Periodico di cultura e di informazione numismatica 
\item[Numizmaticar-long] Numizmatičar. Casopis za anticki i stari jugoslavenski novac %*Abweichung!
\item[Nummus-long] Nummus. Sociedade portuguesa de numismatica 
\item[NumZ-long] Numismatische Zeitschrift 
\item[NuovDidask-long] Nuovo Didaskaleion 
\item[OccasPublClSt-long] Occasional Publications in Classical Studies 
\item[OccOr-long] Occident and Orient 
\item[OGIS-long] W. Dittenberger, Orientis Graeci inscriptiones selectae (Leipzig 1903--­1905) 
\item[OeJh-long] Jahreshefte des Österreichischen Archäologischen Institutes in Wien %*Abweichung!
\item[OF-long] Olympische Forschungen 
\item[Offa-long] Offa. Berichte und Mitteilungen zur Urgeschiche, Frühgeschichte und Mittelalterarchäologie 
\item[Ogam-long] Ogam. Bulletin des Amis de la tradition celtique 
\item[Oikumene-long] Oikumene. Studia ad historiam antiquam classicam et orientalem pertinentia 
\item[OIP-long] Oriental Institute Publications 
\item[Olba-long] Olba. Mersin Üniversitesi Kilikia Arkeolojisini Araştırma Merkezi yayınları 
\item[OlBer-long] Bericht über die Ausgrabungen in Olympia 
\item[Olympia-long] Olympia. Die Ergebnisse der von dem Deutschen Reich veranstalteten Ausgrabung (Berlin 1890--­1897) 
\item[Olynthus-long] Excavations at Olynthus 
\item[OLZ-long] Orientalistische Literaturzeitung 
\item[OpArch-long] Skrifter utgivna av Svenska institutet i Rom. Opuscula archaeologica 
\item[OpAth-long] Opuscula Atheniensia 
\item[OpFin-long] Opuscula Instituti Romani Finlandiae 
\item[OpPomp-long] Opuscula Pompeiana 
\item[OpRom-long] Opuscula Romana 
\item[Opus-long] Opus. Rivista internazionale per la storia economica e sociale dell’antichità 
\item[Or-long] Orientalia (Pontificio Istituto biblico) 
\item[OrA-long] Orient-Archäologie 
\item[OrAnt-long] Oriens antiquus. Rivista del Centro per le antichità e la storia dell’arte del Vicino Oriente 
\item[OrbTerr-long] Orbis terrarum. Internationale Zeitschrift für historische Geographie der Alten Welt 
\item[OrChr-long] Oriens christianus 
\item[OrChrPer-long] Orientalia christiana periodica 
\item[Ordona-long] Ordona. Rapports et études 
\item[Orient-long] Orient. The Reports of the Society for Near Eastern Studies in Japan 
\item[Origini-long] Origini. Preistoria e protostoria delle civiltà antiche 
\item[Orizzonti-long] Orizzonti. Rassegna di archeologia 
\item[Orpheus-long] Orpheus. Rivista di umanità classica e cristiana 
\item[OrpheusThracSt-long] Orpheus. Journal of Indo-European, Palaeo-Balkan and Thracian Studies 
\item[OrSu-long] Orientalia Suecana. An International Journal of Indological, Iranian, Semitic, Turkic Studies 
\item[OsjZbor-long] Osjekizbornik 
\item[OstbGrenzm-long] Ostbairische Grenzmarken. Passauer Jahrbuch für Geschichte, Kunst und Volkskunde 
\item[Ostraka-long] Ostraka. Rivista di antichità 
\item[OudhMeded-long] Oudheidkundige mededelingen uit het Rijksmuseum van oudheden te Leiden 
\item[OxfJA-long] Oxford Journal of Archaeology 
\item[OxfStPhilos-long] Oxford Studies in Ancient Philosophy 
\item[Pact-long] Pact. Revue du Groupe européen d’études pour les techniques physiques, chimiques et mathématiques appliquées à l’archéologie 
\item[Padusa-long] Padusa. Bolletino del Centro polesano di studi storici, archeologici ed etnografici, Rovigo 
\item[PagA-long] Pagine di archeologia. Studi e materiali 
\item[PAI-long] Polevye archeologičeskie issledovanija 
\item[Paideuma-long] Paideuma. Mitteilungen zur Kulturkunde 
\item[Palaeohistoria-long] Palaeohistoria. Acta et communicationes Instituti bio-archaeologici universitatis Groninganae 
\item[Paleohispanica-long] Paleohispánica. Revista sobre lenguas y culturas de la Hispania antigua %*Abweichung!
\item[Palladio-long] Palladio. Rivista di storia dell’architettura 
\item[Pallas-long] Pallas. Revue d’études antiques 
\item[Palmet-long] Palmet. Sadberk Hanım Müzesi yıllığı 
\item[PamA-long] Památky archeologické 
\item[Pan-long] Pan. Studi dell’Istituto di filologia latina 
\item[PapBilb-long] Papeles Bilbilitanos 
\item[Papyri-long] Papyri. Bollettino del Museo del papiro 
\item[Parthica-long] Parthica. Incontri di culture nel mondo antico 
\item[Partenope-long] Partenope. Rivista trimestrale di cultura napoletana 
\item[PAS-long] Prähistorische Archäologie in Südosteuropa 
\item[PBF-long] Prähistorische Bronzefunde 
\item[Pegasus-long] Pegasus. Berliner Beiträge zum Nachleben der Antike 
\item[PEQ-long] Palestine Exploration Quarterly 
\item[Peristil-long] Peristil. Zbornik radova za povijest umjetnosti 
\item[Persica-long] Persica. Jaarboek van het Genootschap Nederland-Iran, Stichting voor culturele betrekkingen 
\item[Peuce-long] Peuce. Studii şi comunicări de istorie veche, arheologie şi numismatică 
\item[PF-long] Pergamenische Forschungen 
\item[Pharos-long] Pharos. Journal of the Netherlands Institute at Athens 
\item[Philologus-long] Philologus. Zeitschrift für das klassische Altertum 
\item[Phoenix-long] Phoenix. The Journal of the Classical Association of Canada 
\item[PhoenixExOrLux-long] Phoenix. Bulletin uitgegeven door het Vooraziatisch-Egyptisch Genootschap »Ex Oriente Lux« 
\item[Phoibos-long] Phoibos. Bulletin du Cercle de philologie classique et orientale de l’Université libre de Bruxelles 
\item[Phronesis-long] Phronesis. A Journal for Ancient Philosophy 
\item[Picus-long] Picus. Studi e ricerche sulle Marche nell’antichità 
\item[PIR-long] Prosopographia Imperii Romani 
\item[PKG-long] Propyläen Kunstgeschichte 
\item[Platon-long] Πλάτον. Δελτίον της Εταιρείας Ελλήνων Φιλολόγων 
\item[PLup-long] Papyrologica Lupiensia 
\item[PolAMed-long] Polish Archaeology in the Mediterranean 
\item[Polemon-long] Πολέμων. Αρχαιολογικόν Περιοδικόν 
\item[Polis-long] Polis. Revista de ideas y formas políticas de la antigüedad clásica 
\item[PompHercStab-long] Pompeii, Herculaneum, Stabiae. Bolletino. Associazione internazionale Amici di Pompei 
\item[Pontica-long] Pontica. Studii şi materiale de istorie, arheologie şi muzeografie, Constanţa 
\item[Portugalia-long] Portugália. Revista do Instituto de arqueologia da Faculdade de letras da Universidade do Porto 
\item[PP-long] La parola del passato 
\item[PPM-long] Pompei: Pitture e mosaici. Enciclopedia dell’arte antica classica e orientale 
\item[PraceA-long] Prace archeologiczne 
\item[PraceMatLodz-long] Prace i materialy Muzeum archeologicznego i etnograficznego w Łodzi %*Abweichung!
\item[Prakt-long] Πρακτικά της εν Αθήναις Αρχαιολογικής Εταιρείας 
\item[PraktAkAth-long] Πρακτικά της Ακαδημίας Αθηνών 
\item[PreistAlp-long] Preistoria alpina. Museo tridentino di scienze naturali 
\item[PriloziZagreb-long] Prilozi Instituta za arheologiju u Zagrebu 
\item[PrincViana-long] Principe di Viana 
\item[ProblIsk-long] Problemi na izkustvoto. Trimesecno spisanie za estetika, teorija, istorija i kritika na izkustvoto 
\item[ProcAfrClAss-long] The Proceedings of the African Classical Associations 
\item[ProcCambrPhilSoc-long] Proceedings of the Cambridge Philological Society 
\item[ProcDanInstAth-long] Proceedings of the Danish Institute at Athens 
\item[ProcPrehistSoc-long] Proceedings of the Prehistoric Society 
\item[Prometheus-long] Prometheus. Rivista quadrimestrale di studi classici 
\item[ProspAQuad-long] Prospezioni archeologiche. Quaderni 
\item[Prospettiva-long] Prospettiva. Rivista di storia dell’arte antica e moderna 
\item[Prospezioni-long] Prospezioni. Bollettino di informazioni scientifiche 
\item[ProvHist-long] Provence historique 
\item[ProvLucca-long] La provincia di Lucca 
\item[PublInstTTMeneses-long] Publicaciones de la Institución »Tello Téllez de Meneses« 
\item[Pulpudeva-long] Pulpudeva. Semaines philippopolitaines de l’histoire et de la culture thrace 
\item[Puteoli-long] Puteoli. Studi di storia antica 
\item[Pyrenae-long] Pyrenae. Crónica arqueológica 
\item[PZ-long] Prähistorische Zeitschrift 
\item[QDAP-long] The Quarterly of the Department of Antiquities in Palestine 
\item[QuadABarcel-long] Quaderns d’arqueologia i història de la ciutat (Barcelona) 
\item[QuadACagl-long] Quaderni. Soprintendenza archeologica per la provincie di Cagliari e Oristano 
\item[QuadACal-long] Quaderni del Dipartimento delle arti, Università della Calabria 
\item[QuadALibya-long] Quaderni di archeologia della Libia 
\item[QuadAMant-long] Quaderni di archeologia del Mantovano 
\item[QuadAMess-long] Quaderni di archeologia, Università di Messina 
\item[QuadAOst-long] Quaderni del Gruppo archeologico ostigliese 
\item[QuadAPiem-long] Quaderni della Soprintendenza archeologica del Piemonte 
\item[QuadAquil-long] Quaderni aquileiesi 
\item[QuadAReggio-long] Quaderni d’archeologia reggiana 
\item[QuadAVen-long] Quaderni di archeologia del Veneto 
\item[QuadCast-long] Quaderns de prehistòria i arqueologia de Castelló 
\item[QuadCat-long] Quaderni catanesi di studi classici e medievali 
\item[QuadChieti-long] Quaderni dell’Istituto di archeologia e storia antica, Università di Chieti 
\item[QuadErb-long] Quaderni erbesi. Civico museo archeologico di Erba 
\item[QuadFriulA-long] Quaderni friulani di archeologia 
\item[QuadGerico-long] Quaderni di Gerico 
\item[QuadIstFilGr-long] Quaderni dell’Istituto di filologia greca 
\item[QuadIstLat-long] Quaderni dell’Istituto di lingua e letteratura latina, Università di Roma 
\item[QuadLecce-long] Quaderni. Istituto di lingue e letterature classiche, Facoltà di magistero, Università degli studi, Lecce 
\item[QuadMusPontecorvo-long] Museo civico Pontecorvo. Quaderni 
\item[QuadMusSalinas-long] Quaderni del Museo archeologico regionale Antonino Salinas 
\item[QuadProtost-long] Quaderni di protostoria. Università di Perugia 
\item[QuadStLun-long] Quaderni. Centro studi lunensi 
\item[QuadStor-long] Quaderni di storia 
\item[QuadStorici-long] Quaderni storici 
\item[QuadUrbin-long] Quaderni urbinati di cultura classica 
\item[Quaternaria-long] Quaternaria. Storia naturale e culturale del quaternario 
\item[RA-long] Revue archéologique 
\item[RAArtLouv-long] Revue des archéologues et historiens d’art de Louvain 
\item[RAC-long] Reallexikon für Antike und Christentum 
\item[RACFr-long] Revue archéologique du Centre de la France 
\item[RAComo-long] Rivista archeologica dell’antica provincia e diocesi di Como 
\item[RACr-long] Rivista di archeologia cristiana 
\item[RadAkZadar-long] Radovi Zavoda za povijesne znanosti, Hrvatska akademija znanosti i umjetnosti u Zadru 
\item[Radiocarbon-long] Radiocarbon. An International Journal of Cosmogenic Isotope Research 
\item[RadSplit-long] Radovi. Razdio povijesnih znanosti 
\item[RAE-long] Revue archéologique de l’Est et du Centre-Est 
\item[Raggi-long] Raggi. Zeitschrift für Kunstgeschichte und Archäologie 
\item[RAMadrid-long] Revista de arqueología 
\item[RANarb-long] Revue archéologique de Narbonnaise 
\item[RAPon-long] Revista d’arqueologia de Ponent 
\item[RapWyk-long] Raporty wykopaliskowe 
\item[RArchBiblMus-long] Revista de archivos, bibliotecas y museos 
\item[RArcheom-long] Revue d’archéométrie 
\item[RArtMus-long] La revue des arts. Musées de France 
\item[RassAPiomb-long] Rassegna di archeologia. Associazione archeologica piombinese 
\item[RassLazio-long] Rassegna del Lazio 
\item[RassStorSalern-long] Rassegna storica salernitana 
\item[RassVolt-long] Rassegna volterrana 
\item[RAssyr-long] Revue d’assyriologie et d’archéologie orientale 
\item[Ratiariensia-long] Ratiariensia. Studi e materiali mesici e danubiani 
\item[RAtlMed-long] Revista atlántica-mediterránea de prehistoria y arqueología social 
\item[RavStRic-long] Ravenna studi e ricerche 
\item[Raydan-long] Raydan. Journal of the Ancient Yemeni Antiquities and Epigraphy 
\item[RB-long] Revue biblique 
\item[RBelgNum-long] Revue belge de numismatique et de sigillographie 
\item[RBelgPhilHist-long] Revue belge de philologie et d’histoire 
\item[RBK-long] Reallexikon zur byzantinischen Kunst 
\item[RCulClMedioev-long] Rivista di cultura classica e medioevale 
\item[RdA-long] Rivista di archeologia 
\item[RDAC-long] Report of the Department of Antiquities, Cyprus 
\item[RdE-long] Revue d’égyptologie (Kairo) 
\item[RDroitsAnt-long] Revue internationale des droits de l’antiquité 
\item[RE-long] Paulys Realencyclopädie der classischen Altertumswissenschaft 
\item[REA-long] Revue des études anciennes 
\item[REByz-long] Revue des études byzantines 
\item[RecConstantine-long] Recueil des notices et memoires de la Société archéologique du département de Constantine 
\item[RechACrac-long] Recherches archéologiques. Institut d’archéologie de l’Université de Cracovie 
\item[RechAlb-long] Recherches albanologiques 
\item[RecMusAlcoi-long] Recerques del Museu d’Alcoi 
\item[RecTrav-long] Recueil de travaux relatifs à philologie et l’archéologie égyptiennes et assyriennes 
\item[REG-long] Revue des études grecques 
\item[ReiCretActa-long] Rei Cretariae Romanae Fautorum acta 
\item[ReiCretCommunic-long] Rei Cretariae Romanae Fautores. Communicationes 
\item[REL-long] Revue des études latines 
\item[Rema-long] Ρήμα. Mitteilungen zur indogermanischen, vornehmlich indo-iranischen Wortkunde sowie zur holothetischen Sprachtheorie 
\item[RendBologna-long] Atti della Accademia delle scienze dell’Istituto di Bologna. Rendiconti 
\item[RendIstLomb-long] Rendiconti. Classe di lettere e scienze morali e storiche, Istituto lombardo, Accademia di scienze e lettere 
\item[RendLinc-long] Rendiconti dell’Accademia nazionale dei Lincei, Classe di scienze morali, storiche e filologiche 
\item[RendNap-long] Rendiconti della Accademia di archeologia, lettere e belle arti, Napoli 
\item[RendPontAc-long] Rendiconti. Atti della Pontificia accademia romana di archeologia 
\item[RepMalta-long] Report on the Working of the Museum Department, Malta, Department of Information 
\item[Reppal-long] Reppal. Revue des études phénicienne-puniques et des antiquités libyques 
\item[RepSocLibSt-long] Annual Report. The Society for Libyan Studies 
\item[RES-long] Répertoire d’épigraphie sémitique (Paris 1900--1950) 
\item[REstIber-long] Revista de estudios ibéricos 
\item[REtArm-long] Revue des études arméniennes 
\item[RevEg-long] Revue égyptologique (Paris) 
\item[RFil-long] Rivista di filologia e di istruzione classica 
\item[RGeorgCauc-long] Revue des études géorgiennes et caucasiennes 
\item[RGF-long] Römisch-Germanische Forschungen 
\item[RGuimar-long] Revista de Guimarães 
\item[RHA-long] Revue hittite et asianique 
\item[RheinMusBonn-long] Das Rheinische Landesmuseum Bonn. Berichte aus der Arbeit des Museums 
\item[RHistArmees-long] Revue historique des armées %*Abweichung!
\item[RHistRel-long] Revue de l’histoire des religions 
\item[RhM-long] Rheinisches Museum für Philologie 
\item[RIA-long] Rivista dell’Istituto nazionale d’archeologia e storia dell’arte 
\item[RIC-long] H. Mattingly – E. A. Sydenham, The Roman Imperial Coinage 
\item[RicEgAntCopt-long] Ricerche di egittologia e di antichità copte 
\item[RicognA-long] Ricognizioni archeologiche 
\item[RicStBrindisi-long] Ricerche e studi. Museo Francesco Ribezzo, Brindisi 
\item[RIngIntem-long] Rivista Ingauna e Intemelia 
\item[RItNum-long] Rivista italiana di numismatica e scienze affini 
\item[RlA-long] Reallexikon der Assyriologie und vorderasiatischen Archäologie 
\item[RLouvre-long] Revue du Louvre. La revue des musées de France 
\item[RM-long] Mitteilungen des Deutschen Archäologischen Instituts, Römische Abteilung 
\item[RNum-long] Revue numismatique 
\item[RoczMuzWarsz-long] Rocznik Muzeum narodowego w Warszawie 
\item[RoemOe-long] Römisches Österreich. Jahresschrift der Österreichischen Gesellschaft für Archäologie %*Abweichung!
\item[RoemQSchr-long] Römische Quartalschrift für christliche Altertumskunde und Kirchengeschichte %*Abweichung!
\item[Romanobarbarica-long] Romanobarbarica. Contributi allo studio dei rapporti culturali tra il mondo latino e mondo barbarico 
\item[RomGens-long] Romana gens. Bollettino dell’Associazione archeologica romana 
\item[RoscherML-long] W. H. Roscher, Ausführliches Lexikon der griechischen und römischen Mythologie %*Abweichung!
\item[RossA-long] Rossijskaja archeologija 
\item[RPC-long] Roman Provincial Coinage 
\item[RPhil-long] Revue de philologie, de littérature et d’histoire anciennes 
\item[RPortA-long] Revista portuguesa de arqueologia 
\item[RPorto-long] Revista da Facultade de letras. Serie de historia. Universidade do Porto 
\item[RRC-long] M. Crawford, Roman Republican Coinage (London 1974) 
\item[RSaintonge-long] Revue de la Saintonge et de l’Aunis 
\item[RScPreist-long] Rivista di scienze preistoriche 
\item[RSO-long] Rivista degli studi orientali 
\item[RStBiz-long] Rivista di studi bizantini e neoellenici 
\item[RStCl-long] Rivista di studi classici 
\item[RStFen-long] Rivista di studi fenici 
\item[RStLig-long] Rivista di studi liguri 
\item[RStMarch-long] Rivista di studi marchigiani 
\item[RStorAnt-long] Rivista storica dell’antichità 
\item[RStorCal-long] Rivista storica calabrese 
\item[RStPomp-long] Rivista di studi pompeiani 
\item[RStPun-long] Rivista di studi punici 
\item[RTopAnt-long] Rivista di topografia antica 
\item[Rudiae-long] Rudiae. Ricerche sul mondo classico 
\item[SaalbJb-long] Saalburg-Jahrbuch. Bericht des Saalburg-Museums 
\item[SaarBeitr-long] Saarbrücker Beiträge zur Altertumskunde 
\item[SaarStMat-long] Saarbrücker Studien und Materialien zur Altertumskunde 
\item[Sacer-long] Sacer. Bollettino della Associazione storica saccarese 
\item[Saeculum-long] Saeculum. Jahrbuch für Universalgeschichte 
\item[SAGA-long] Studien zur Archäologie und Geschichte Altägyptens 
\item[SaggiFen-long] Saggi fenici 
\item[Saguntum-long] Saguntum. Papeles del Laboratorio de arqueología de Valencia 
\item[Saitabi-long] Saitabi. Noticiario de historia, arte y arqueología de Levante 
\item[SAK-long] Studien zur altägyptischen Kultur 
\item[Salduie-long] Salduie. Estudios de prehistoria y arqueología 
\item[Samothrace-long] Samothrace. Excavations Conducted by the Institute of Fine Arts of New York University 
\item[Sandalion-long] Sandalion. Quaderni di cultura classica, cristiana e medievale 
\item[Sardis-long] Sardis. Publications of the American Society for the Excavation of Sardis 
\item[Sargetia-long] Sargetia. Acta Musei regionalis Devensis 
\item[SarkSt-long] Sarkophag-Studien 
\item[Sautuola-long] Sautuola. Revista del Instituto de prehistoria y arqueologia Sautuola 
\item[Savaria-long] Savaria. Bulletin der Museen des Komitats Vas 
\item[SBBerlin-long] Sitzungsberichte der Deutschen Akademie der Wissenschaften zu Berlin. Klasse für Sprache, Literatur und Kunst 
\item[SBLeipzig-long] Sitzungsberichte der Sächsischen Akademie der Wissenschaften zu Leipzig 
\item[SBMuenchen-long] Bayerische Akademie der Wissenschaften. Philosophisch-Historische Klasse. Sitzungsberichte %*Abweichung!
\item[SborBrno-long] Sborník prací Filozofické fakulty Brněnské univerzity. M, Rada archeologická 
\item[SBWien-long] Sitzungsberichte. Österreichische Akademie der Wissenschaften 
\item[ScAnt-long] Scienze dell’antichità. Storia, archeologia, antropologia 
\item[SCE-long] The Swedish Cyprus Expedition 
\item[SchildStei-long] Schild von Steier. Beiträge zur Steirischen Vor- und Frühgeschichte und Münzkunde 
\item[Scholia-long] Scholia. Natal Studies in Classical Antiquity 
\item[SchwMueBl-long] Schweizer Münzblätter %*Abweichung!
\item[SchwNumRu-long] Schweizerische numismatische Rundschau 
\item[ScrCiv-long] Scrittura e civiltà 
\item[ScrClIsr-long] Scripta classica Israelica. Yearbook of the Israel Society for the Promotion of Classical Studies 
\item[ScrHieros-long] Scripta Hierosolymitana. Publications of the Hebrew University, Jerusalem 
\item[ScrMed-long] Scripta mediterranea. Bulletin of the Society for Mediterranean Studies, Toronto 
\item[SDAIK-long] Sonderschriften des Deutschen Archäologischen Instituts, Abteilung Kairo 
\item[SEG-long] Supplementum epigraphicum Graecum 
\item[SeminRom-long] Seminari romani di cultura greca 
\item[Semitica-long] Semitica. Cahiers publiés par l’Institut d’études sémitiques du College de France. Avec le concours du Centre national de la recherche scientifique 
\item[SetubalA-long] Setúbal arqueológica 
\item[Sibrium-long] Sibrium. Collana di studi e documentazioni 
\item[SicA-long] Sicilia archeologica 
\item[SicGymn-long] Siculorum gymnasium 
\item[SIG-long] W. Dittenberger, Sylloge inscriptionum Graecarum (Leipzig 1915--­1924) 
\item[Sileno-long] Sileno. Rivista di studi classici e cristiani 
\item[SilkRoadArtA-long] Silk Road Art and Archaeology. Journal of the Institute of Silk Road Studies, Kamakura 
\item[SIMA-long] Studies in Mediterranean Archaeology 
\item[Simblos-long] Simblos. Scritti di storia antica 
\item[Skyllis-long] Skyllis. Zeitschrift für Unterwasserarchäologie 
\item[SlovA-long] Slovenská archeológia 
\item[SlovNum-long] Slovenská numizmatika 
\item[SMEA-long] Studi micenei ed egeo-anatolici 
\item[SNG-long] Sylloge nummorum Graecorum 
\item[SocGeoAOran-long] (Bulletin trimestriel de la) Société de géographie et d’archéologie (de la province) d’Oran 
\item[SoobErmit-long] Soobščenija Gosudarstvennogo Ėrmitaža 
\item[SoobMuzMoskva-long] Soobščenija Gosudarstvennogo muzeja izobrazitel’nych isskustv imeni A. S. Puškina 
\item[SovA-long] Sovetskaja archeologija 
\item[Spal-long] Spal. Revista de prehistoria y arqueología de la Universidad de Sevilla 
\item[SpNov-long] Specimina nova dissertationum ex Instituto historico Universitatis Quinqueecclesiensis de Iano Pannonio nominatae 
\item[Spoletium-long] Spoletium. Rivista di arte, storia, cultura 
\item[StA-long] Studia archaeologica 
\item[Stadion-long] Stadion. Internationale Zeitschrift für Geschichte des Sports 
\item[StaedelJb-long] Städel-Jahrbuch %*Abweichung!
\item[StAeg-long] Studia Aegyptiaca. Budapest 
\item[StAlb-long] Studia Albanica 
\item[StAnt-long] Studi di antichità. Università di Lecce 
\item[Starinar-long] StarinarArheoloki institut Beograd 
\item[StAWarsz-long] Studia archeologiczne. Uniwersytet Warszawski, Instytut archeologii 
\item[StBiFranc-long] Studium biblicum Franciscanum. Liber annuus 
\item[StBitont-long] Studi bitontini 
\item[StBoT-long] Studien zu den Bogazköy-Texten 
\item[StCercIstorV-long] Studii şi cercetări de istorie veche şi arheologie 
\item[StCercNum-long] Studii şi cercetări de numismatică 
\item[StCl-long] Studii clasice. Societatea de studii clasice din Republica socialistă Romănia 
\item[StClOr-long] Studi classici e orientali 
\item[StDocA-long] Studi e documenti di archeologia 
\item[StDocHistIur-long] Studia et documenta historiae et iuris 
\item[StEbla-long] Studi eblaiti 
\item[StEgAntPun-long] Studi di egittologia e di antichità puniche 
\item[SteMat-long] Studi e materiali. Soprintendenza ai beni archeologici per la Toscana 
\item[StEpigrLing-long] Studi epigrafici e linguistici sul Vicino Oriente antico 
\item[StEtr-long] Studi etruschi 
\item[StGenu-long] Studi genuensi 
\item[StHist-long] Studia historica. Historia antigua 
\item[StiftHambKuSamml-long] Stiftung zur Förderung der Hamburgischen Kunstsammlungen. Erwerbungen 
\item[StItFilCl-long] Studi italiani di filologia classica 
\item[StLatIt-long] Studi latini e italiani 
\item[StMagreb-long] Studi magrebini 
\item[StMatStorRel-long] Studi e materiali di storia delle religioni 
\item[StOliv-long] Studia Oliveriana 
\item[StOr-long] Studia orientalia, Helsinki 
\item[StOrCr-long] Studi sull’Oriente cristiano 
\item[StP-long] Studia papyrologica 
\item[StrennaRom-long] Strenna dei romanisti 
\item[StRom-long] Studi romani 
\item[StRomagn-long] Studi romagnoli 
\item[StSalent-long] Studi salentini 
\item[StSard-long] Studi sardi 
\item[StStorRel-long] Studi storico-religiosi 
\item[StTardoant-long] Studi tardoantichi 
\item[StTrentStor-long] Studi trentini di scienze storiche. Sezione seconda 
\item[StTroica-long] Studia Troica 
\item[StUrbin-long] Studi urbinati. B, Scienze umane. 3, Linguistica, letteratura, arte 
\item[Sumer-long] Sumer. A Journal of Archaeology (and History) in Iraq 
\item[SylvaMala-long] Sylva Mala. Bollettino del Centro di studi archeologici di Boscoreale, Boscotrecase e Trecase %*Abweichung!
\item[SymbOslo-long] Symbolae Osloenses 
\item[Syria-long] Syria. Revue d’art oriental et d’archéologie 
\item[SyrMesopSt-long] Syro-Mesopotamian Studies 
\item[TAD-long] Türk arkeoloji dergisi 
\item[Talanta-long] Τάλαντα. Proceedings of the Dutch Archaeological and Historical Society 
\item[TAM-long] E. Kalinka (Hrsg.), Tituli Asiae Minoris (Wien 1901--­1941) 
\item[Taras-long] Taras. Rivista di archeologia 
\item[Tarsus-long] Excavations at Gözlü Kule, Tarsus 
\item[TAVO-long] Tübinger Atlas des Vorderen Orients 
\item[TeherF-long] Teheraner Forschungen 
\item[Teiresias-long] Teiresias. A Review and Continuing Bibliography of Boiotian Studies 
\item[TelAvivJA-long] Tel Aviv. Journal of the Institute of Archaeology of Tel Aviv University 
\item[TerraAntBalc-long] Acta Associationis internationalis »Terra antiqua balcanica« 
\item[TerraVolsci-long] Terra dei Volsci. Annali del Museo archeologico di Frosinone 
\item[Teruel-long] Teruel. Instituto de estudios turolenses 
\item[TextilAnc-long] Textiles anciens. Bulletin du Centre international d’étude des textiles anciens 
\item[TheolRu-long] Theologische Rundschau 
\item[ThesCRA-long] Thesaurus Cultus et Rituum Antiquorum 
\item[Thessalika-long] Θεσσαλικά 
\item[Thessalonike-long] Η Θεσσαλονίκη 
\item[Thieme-Becker-long] U. Thieme – F. Becker (Hrsg.), Allgemeines Lexikon der bildenden Künstler %*Abweichung!
\item[ThrakChron-long] Θρακικά Χρονικά 
\item[ThrakEp-long] Θρακική Επετηρίδα 
\item[TIB-long] Tabula Imperii Byzantini 
\item[Tibiscus-long] Tibiscus. Istorie, arheologie. Muzeul Banatului Timişoara 
\item[TiLeon-long] Tierras de León 
\item[Tiryns-long] Tiryns. Forschungen und Berichte 
\item[TMA-long] Tijdschrift voor Mediterrane archeologie 
\item[Topoi-long] Τόποι. Orient – Occident 
\item[Torretta-long] La torretta. Rivista quadrimestrale a cura della Biblioteca comunale di Blera 
\item[TourOrleOr-long] La Tour de l’Orle-d’Or, Semur-en-Auxois 
\item[TrabAntrEtn-long] Trabalhos de antropologia e etnologia 
\item[TrabArq-long] Trabalhos de arqueologia 
\item[TrabAssArqPort-long] Trabalhos da associação dos arqueólogos portugueses 
\item[TrabNavarra-long] Trabajos de arqueología de Navarra 
\item[TrabPrehist-long] Trabajos de prehistoria 
\item[Traditio-long] Traditio. Studies in Ancient and Medieval History, Thought and Religion 
\item[TransactAmPhilAss-long] Transactions and Proceedings of the American Philological Association 
\item[TransactAmPhilosSoc-long] Transactions of the American Philosophical Society 
\item[TransactLond-long] Transactions of the London and Middlesex Archaeological Society 
\item[TravMem-long] Travaux et mémoires. Centre de recherche d’histoire et civilisation byzantine, Paris 
\item[TravToulouse-long] Travaux de l’Institut d’art préhistorique, Université de Toulouse – Le Mirail 
\item[TreMonet-long] Trésors monétaires 
\item[TribArq-long] Tribuna d’arqueologia 
\item[TrudyErmit-long] Trudy Gosudarstvennogo Ėrmitaža 
\item[TrWPr-long] Trierer Winckelmannsprogramme 
\item[TrZ-long] Trierer Zeitschrift für Geschichte und Kunst des Trierer Landes und seiner Nachbargebiete 
\item[TTKY-long] Türk Tarih Kurumu yayınları 
\item[TueBA-Ar-long] Türkiye Bilimler Akademisi arkeoloji dergisi %*Abweichung!
\item[Tyche-long] Tyche. Beiträge zur Alten Geschichte, Papyrologie und Epigraphik 
\item[UF-long] Ugarit-Forschungen. Internationales Jahrbuch für die Altertumskunde Syrien-Palästinas 
\item[UPA-long] Universitätsforschungen zur Prähistorischen Archäologie 
\item[LUrbe-long] L’Urbe. Rivista romana %*Abweichung!
\item[UrSchw-long] Ur-Schweiz. La Suisse primitive 
\item[UVB-long] Vorläufiger Bericht über die von dem Deutschen Archäologischen Institut und der Deutschen Orient-Gesellschaft aus den Mitteln der Deutschen Forschungsgemeinschaft unternommenen Ausgrabungen in Uruk-Warka 
\item[VarSpom-long] Varstvo spomenikov 
\item[VDI-long] Vestnik drevnej istorii 
\item[Vekove-long] Vekove. Dvumesečno spisanie. Bălgarsko istoričesko družestvo 
\item[Veleia-long] Veleia. Revista de prehistoria, historia antigua, arqueología y filología clásicas 
\item[VenArt-long] Venezia arti. Bolletino del Dipartimento di storia e critica delle arti dell’Università di Venezia 
\item[VerAmstMeded-long] Mededelingenblad. Vereniging van Vrienden Allard Pierson Museum 
\item[Verbanus-long] Verbanus. Rassegna per la cultura, l’arte, la storia del lago 
\item[VeteraChr-long] Vetera christianorum 
\item[VGesVind-long] Veröffentlichungen der Gesellschaft Pro Vindonissa 
\item[Vichiana-long] Vichiana. Rassegna di studi filologici e storici 
\item[VicOr-long] Vicino Oriente 
\item[VigChr-long] Vigiliae christianae 
\item[Viminacium-long] Viminacium. Zbornik radova Narodnog muzeja 
\item[VisRel-long] Visible Religion 
\item[Vitudurum-long] Beiträge zum römischen Oberwinterthur – Vitudurum. Ausgrabungen im Unteren Bühl 
\item[VivScyl-long] Vivarium Scyllacense. Bollettino dell’Istituto di studi su Cassiodoro e sul medioevo in Calabria 
\item[VizVrem-long] Vizantijskij vremennik 
\item[VjesAMuzZagreb-long] Vjesnik Arheološkog muzeja u Zagrebu 
\item[VjesDal-long] Vjesnik za arheologiju i historiju dalmatinsku. Bulletin d’archéologie et d’histoire dalmates 
\item[Wad-al-Hayara-long] Wad-al-Hayara. Revista de estudios de la Institución provincial de cultura »Marqués de Santillana« de Guadalajara 
\item[WeltGesch-long] Die Welt als Geschichte 
\item[WiadA-long] Wiadomości archeologiczne. Bulletin archéologique polonais 
\item[WissMBosn-long] Wissenschaftliche Mitteilungen des Bosnischen Landesmuseums, A. Archäologie 
\item[WissZBerl-long] Wissenschaftliche Zeitschrift der Humboldt-Universität zu Berlin. Gesellschafts- und sprachwissenschaftliche Reihe 
\item[WissZHalle-long] Wissenschaftliche Zeitschrift. Martin-Luther-Universität Halle-Wittenberg 
\item[WissZJena-long] Wissenschaftliche Zeitschrift der Friedrich-Schiller-Universität Jena 
\item[WissZRostock-long] Wissenschaftliche Zeitschrift der Universität Rostock 
\item[WO-long] Die Welt des Orients. Wissenschaftliche Beiträge zur Kunde des Morgenlandes 
\item[WorldA-long] World Archaeology 
\item[WSt-long] Wiener Studien 
\item[WuerzbJb-long] Würzburger Jahrbücher für die Altertumswissenschaft %*Abweichung!
\item[WVDOG-long] Wissenschaftliche Veröffentlichungen der Deutschen Orient-Gesellschaft 
\item[WZKM-long] Wiener Zeitschrift für die Kunde des Morgenlandes 
\item[Xenia-long] Xenia. Semestrale di antichità 
\item[XeniaAnt-long] Xenia antiqua 
\item[XeniaKonst-long] Xenia. Konstanzer althistorische Vorträge und Forschungen 
\item[YaleClSt-long] Yale Classical Studies 
\item[YaleUnivB-long] Yale University Art Gallery Bulletin 
\item[ZA-long] Zeitschrift für Assyriologie und vorderasiatische Archäologie 
\item[ZAAK-long] Zeitschrift für Archäologie Außereuropäischer Kulturen 
\item[ZAeS-long] Zeitschrift für ägyptische Sprache und Altertumskunde %*Abweichung!
\item[ZAKSSchriften-long] Schriften des Zentrums für Archäologie und Kulturgeschichte des Schwarzmeerraumes 
\item[ZAntChr-long] Zeitschrift für antikes Christentum 
\item[ZAW-long] Zeitschrift für die alttestamentliche Wissenschaft 
\item[ZborMuzBeograd-long] Zbornik Narodnog muzeja Beograd 
\item[ZborRadBeograd-long] Zbornik radova Vizantološkog instituta. Recueil des travaux de l’Institut d’études byzantines, Beograd 
\item[ZborZadar-long] Zbornik Instituta za historijske nauke u Zadru 
\item[ZDMG-long] Zeitschrift der Deutschen Morgenländischen Gesellschaft 
\item[ZDPV-long] Zeitschrift des Deutschen Palästina-Vereins 
\item[Zephyrus-long] Zephyrus. Revista de prehistoria y arqueología 
\item[ZEthn-long] Zeitschrift für Ethnologie der Deutschen Gesellschaft für Völkerkunde und der Berliner Gesellschaft für Anthropologie, Ethnologie und Urgeschichte 
\item[ZfA-long] Zeitschrift für Archäologie 
\item[ZfNum-long] Zeitschrift für Numismatik 
\item[ZivaAnt-long] Živa antika. Antiquité vivante 
\item[ZKuGesch-long] Zeitschrift für Kunstgeschichte 
\item[ZNW-long] Zeitschrift für die neutestamentliche Wissenschaft und die Kunde der älteren Kirche 
\item[ZPE-long] Zeitschrift für Papyrologie und Epigraphik 
\item[ZSav-long] Zeitschrift der Savigny-Stiftung für Rechtsgeschichte. Romanistische Abteilung 
\item[ZSchwA-long] Zeitschrift für Schweizerische Archäologie und Kunstgeschichte 
\item[ZVerglSprF-long] Zeitschrift für vergleichende Sprachforschung 
\end{description}
\end{footnotesize}