%</driver> % /* % ██████ ███████ █████ ██████ ███ ███ ███████ % ▄ ██ ▄██ ██ ██ ██ ██ ██ ██ ████ ████ ██ % ████ ██████ █████ ███████ ██ ██ ██ ████ ██ █████ % ▀ ██ ▀██ ██ ██ ██ ██ ██ ██ ██ ██ ██ ██ % ██ ██ ███████ ██ ██ ██████ ██ ██ ███████ % \markdownRendererEmphasis{/ %<}driver|readme>\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Installation of the bundle}\markdownRendererInterblockSeparator
{}\markdownRendererCodeSpan{archaeologie} is part of the distributions \markdownRendererLink{MiKTeX}{http://www.miktex.org}{http://www.miktex.org}{} and \markdownRendererLink{TeXLive}{http://www.tug.org/texlive}{http://www.tug.org/texlive}{} -- thus, you can easily install it using the respective package manager. If you would like to install \markdownRendererCodeSpan{archaeologie} into your local folder manually, do the following: Go to your terminal, browse to the folder of this bundle and run\markdownRendererInterblockSeparator
{}\markdownRendererCodeSpan{make install}\markdownRendererInterblockSeparator
{}If you are using macOS you will be asked for your user account password for the installation.\markdownRendererInterblockSeparator
{}Further options of this makefile are:\markdownRendererInterblockSeparator
{}\markdownRendererUlBegin
\markdownRendererUlItem \markdownRendererCodeSpan{clean}: deletes all unnecessary files\markdownRendererUlItemEnd 
\markdownRendererUlItem \markdownRendererCodeSpan{cleanbundle}: deletes all files except \markdownRendererCodeSpan{.dtx}, \markdownRendererCodeSpan{.pl}, \markdownRendererCodeSpan{.md}. You will get the plain version of this bundle. This might be helpful if you send the bundle to someone else.\markdownRendererUlItemEnd 
\markdownRendererUlItem \markdownRendererCodeSpan{ctan}: this will create a zip file which can be used to send to CTAN.\markdownRendererUlItemEnd 
\markdownRendererUlItem \markdownRendererCodeSpan{uninstall}: will erase the locally installed files.\markdownRendererUlItemEnd 
\markdownRendererUlEnd \markdownRendererInterblockSeparator
{}This bundle is constantly updated. For hints, errors or suggestions use the GitHub repository \markdownRendererLink{https://github.com/LukasCBossert/biblatex-archaeologie}{https://github.com/LukasCBossert/biblatex-archaeologie}{https://github.com/LukasCBossert/biblatex-archaeologie}{}.\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Changelog}\markdownRendererInterblockSeparator
{}All notable changes to this project will be documented in the README.md. This project \markdownRendererStrongEmphasis{does not} adhere to \markdownRendererLink{Semantic Versioning}{http://semver.org/}{http://semver.org/}{}. The markdown syntax is inspired by the conventions proposed by \markdownRendererLink{keepachangelog.com}{http://keepachangelog.com/}{http://keepachangelog.com/}{}. %</driver|readme> %<*driver>\relax